---
title: "Mixed Effects Models for Methods Paper"
author: "Joe Celebrezze"
date: "4/8/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Loading in necessary packages
```{r, include = FALSE}
library(tidyverse)
select = dplyr::select
library(here)
here = here::here
library(lme4) #for mixed effects models
library(MuMIn)
#Add in packages as necessary so no redundant packages
```

# Loading in datasets
```{r, include = FALSE}
main_df <- read_csv(here("processed-data/compiled-datasets/METHODS/bothmethods_bothlocations_long.csv"))
```

# Data Wrangling
Note: I think the dw_flam_sample values are off. To me, they don't make much sense, so -- instead -- I used lfm and sample weight to calculate dry weight and water weight of the samples. I did so by solving the following system of equations:

sample_wt = dry weight + water weight
lfm = (water weight/dry weight) * 100

```{r}
vd_main_df <- main_df %>% 
  filter(ignition == 1) %>% # Only looking at samples that ignited
  select(fh, tti, ttfg, fd, gd, gti, temp_max, mpa, 
         lfm_outliers_out, spp, model, location, 
         precip_2mo, individual, sample_wt) %>% 
  mutate(dry_wt = sample_wt/(0.01*lfm_outliers_out+1)) %>%  # I know dry_wt was already the name of a column in main_df, but it isn't a useful column and it is a useful name, so I am taking that name for vd_main_df but it means the dry weight of the sample being burned in this case
  mutate(water_wt = sample_wt - dry_wt) %>% 
  na.omit()
  
# I selected all flam. traits (going to do mem for each one) and the water content/status metrics as well as potential random effects in location, time (precip_2mo used as an indication of time), and individual
```

## Normalizing flam. metrics
```{r}
vd_main_df <- vd_main_df %>% 
  mutate(fh_norm = fh/sample_wt, tti_norm = tti/sample_wt, ttfg_norm = ttfg/sample_wt, fd_norm = fd/sample_wt, gd_norm = gd/sample_wt, gti_norm = gti/sample_wt, temp_max_norm = temp_max/sample_wt)
```

# Model Selection
Starting with maximal model and then using dredge() to narrow out predictor variables

## Hot Plate

### No data manipulation

#### Maximal model
```{r}
hpMEMfh <- lmer(data = vd_main_df, subset = model == "HP", fh ~ mpa + spp + sample_wt + lfm_outliers_out + (1|precip_2mo) + (1|location) + (1|individual)) # precip_2mo is a time proxy that represents the amount of precipitation over the past two months

hpMEMtti <- lmer(data = vd_main_df, subset = model == "HP", tti ~ mpa + spp + sample_wt + lfm_outliers_out + (1|precip_2mo) + (1|location) + (1|individual))

hpMEMfd <- lmer(data = vd_main_df, subset = model == "HP", fd ~ mpa + spp + sample_wt + lfm_outliers_out + (1|precip_2mo) + (1|location) + (1|individual))

hpMEMgti <- lmer(data = vd_main_df, subset = model == "HP", gti ~ mpa + spp + sample_wt + lfm_outliers_out + (1|precip_2mo) + (1|location) + (1|individual))

hpMEMttfg <- lmer(data = vd_main_df, subset = model == "HP", ttfg ~ mpa + spp + sample_wt + lfm_outliers_out + (1|precip_2mo) + (1|location) + (1|individual))

hpMEMtemp_max <- lmer(data = vd_main_df, subset = model == "HP", temp_max ~ mpa + spp + sample_wt + lfm_outliers_out + (1|precip_2mo) + (1|location) + (1|individual))

hpMEMgd <- lmer(data = vd_main_df, subset = model == "HP", gd ~ mpa + spp + sample_wt + lfm_outliers_out + (1|precip_2mo) + (1|location) + (1|individual))
```

#### Dredging
```{r}
options(na.action = "na.fail")
# Flame height
hpDREDGEfh <- dredge(hpMEMfh)
head(hpDREDGEfh)
## Keep: sample.wt and spp; AIC = 487.4
# Time to ignition
hpDREDGEtti <- dredge(hpMEMtti)
head(hpDREDGEtti)
## Keep: sample.wt and spp; AIC = 740.3 (note: model with mpa is not significantly worse)
# Flame duration
hpDREDGEfd <- dredge(hpMEMfd)
head(hpDREDGEfd)
## Keep: sample.wt and spp; AIC = 581.5 (note: model with mpa is not significantly worse)
# Glow to ignition
hpDREDGEgti <- dredge(hpMEMgti)
head(hpDREDGEgti)
## Keep: sample weight, mpa and spp; AIC = 751.9
# Time to first glow
hpDREDGEttfg <- dredge(hpMEMttfg)
head(hpDREDGEttfg)
## Keep: sample weight, mpa and spp; AIC = 757.2
# Temp max
hpDREDGEtemp_max <- dredge(hpMEMtemp_max)
head(hpDREDGEtemp_max)
## Keep: sample weight, mpa and spp; AIC = 749.9 (note: model with lfm is not significantly worse)
# Glow duration
hpDREDGEgd <- dredge(hpMEMgd)
head(hpDREDGEgd)
## Keep: sample weight, lfm, mpa and spp; AIC = 868.3 (note: model without lfm is not significantly worse)
```

### Dry Weight and Wet Weight
Because sample weight itself could be split into both dry weight of the sample and water weight of the sample and this could provide us with a bit more information about what exactly is driving the significance of the sample weight, I am going to run models with dry weight and water weight of the samples

I will exclude sample weight (for obvious reasons) but also lfm because lfm is used to calculate water weight and dry weight

#### Models
I went with the name: hpMEMfh2 since this time sample_wt is split into two variables -- dry weight and water weight -- and since this is the second set of models run
```{r}
hpMEMfh2 <- lmer(data = vd_main_df, subset = model == "HP", fh ~ mpa + spp + dry_wt + water_wt + (1|precip_2mo) + (1|location) + (1|individual)) # precip_2mo is a time proxy that represents the amount of precipitation over the past two months

hpMEMtti2 <- lmer(data = vd_main_df, subset = model == "HP", tti ~ mpa + spp + dry_wt + water_wt + (1|precip_2mo) + (1|location) + (1|individual))

hpMEMfd2 <- lmer(data = vd_main_df, subset = model == "HP", fd ~ mpa + spp + dry_wt + water_wt + (1|precip_2mo) + (1|location) + (1|individual))

hpMEMgti2 <- lmer(data = vd_main_df, subset = model == "HP", gti ~ mpa + spp + dry_wt + water_wt + (1|precip_2mo) + (1|location) + (1|individual))

hpMEMttfg2 <- lmer(data = vd_main_df, subset = model == "HP", ttfg ~ mpa + spp + dry_wt + water_wt + (1|precip_2mo) + (1|location) + (1|individual))

hpMEMtemp_max2 <- lmer(data = vd_main_df, subset = model == "HP", temp_max ~ mpa + spp + dry_wt + water_wt + (1|precip_2mo) + (1|location) + (1|individual))

hpMEMgd2 <- lmer(data = vd_main_df, subset = model == "HP", gd ~ mpa + spp + dry_wt + water_wt + (1|precip_2mo) + (1|location) + (1|individual))
```

#### Dredging
Note: if errors pop up here, it could be because the na.action is not set to na.fail; if you re-run the line of code above (in Hot Plate > No data manipulation > Dredging), it should run no problem
```{r}
# Flame height
hpDREDGEfh2 <- dredge(hpMEMfh2)
head(hpDREDGEfh2)
## Keep: water_wt, dry_wt and spp; AIC = 482.4 (note: model w/o water_wt not significantly worse)
# Time to ignition
hpDREDGEtti2 <- dredge(hpMEMtti2)
head(hpDREDGEtti2)
## Keep: water_wt, dry_wt and spp; AIC = 734.5 (note: model with mpa not significantly worse)
# Flame duration
hpDREDGEfd2 <- dredge(hpMEMfd2)
head(hpDREDGEfd2)
## Keep: water_wt, dry_wt and spp; AIC = 577.8 (note: model w/ mpa not sig. worse)
# Glow to ignition
hpDREDGEgti2 <- dredge(hpMEMgti2)
head(hpDREDGEgti2)
## Keep: water_wt, dry_wt, mpa and spp (all variables); AIC = 745.8
# Time to first glow
hpDREDGEttfg2 <- dredge(hpMEMttfg2)
head(hpDREDGEttfg2)
## Keep: water_wt, dry_wt, mpa and spp (all variables); AIC = 750.7
# Temp max
hpDREDGEtemp_max2 <- dredge(hpMEMtemp_max2)
head(hpDREDGEtemp_max2)
## Keep: water_wt, dry_wt, mpa and spp (all variables); AIC = 743
# Glow duration
hpDREDGEgd2 <- dredge(hpMEMgd2)
head(hpDREDGEgd2)
## Keep: water_wt, dry_wt, mpa and spp (all variables); AIC = 861.8 (note:model w/o mpa not sig. worse)
```
Take-aways: It appears that BOTH water weight and dry weight play a role for the hot plate

### Normalized
Normalizing by sample_wt
#### Models
```{r}
hpMEMfh_norm <- lmer(data = vd_main_df, subset = model == "HP", fh_norm ~ mpa + spp + lfm_outliers_out + (1|precip_2mo) + (1|location) + (1|individual))

hpMEMtti_norm <- lmer(data = vd_main_df, subset = model == "HP", tti_norm ~ mpa + spp + lfm_outliers_out + (1|precip_2mo) + (1|location) + (1|individual))

hpMEMfd_norm <- lmer(data = vd_main_df, subset = model == "HP", fd_norm ~ mpa + spp + lfm_outliers_out + (1|precip_2mo) + (1|location) + (1|individual))

hpMEMgti_norm <- lmer(data = vd_main_df, subset = model == "HP", gti_norm ~ mpa + spp + lfm_outliers_out + (1|precip_2mo) + (1|location) + (1|individual))

hpMEMttfg_norm <- lmer(data = vd_main_df, subset = model == "HP", ttfg_norm ~ mpa + spp + lfm_outliers_out + (1|precip_2mo) + (1|location) + (1|individual))

hpMEMtemp_max_norm <- lmer(data = vd_main_df, subset = model == "HP", temp_max_norm ~ mpa + spp + lfm_outliers_out + (1|precip_2mo) + (1|location) + (1|individual))

hpMEMgd_norm <- lmer(data = vd_main_df, subset = model == "HP", gd_norm ~ mpa + spp + lfm_outliers_out + (1|precip_2mo) + (1|location) + (1|individual))
```

#### Dredging
```{r}
# Flame height
hpDREDGEfh_norm <- dredge(hpMEMfh_norm)
head(hpDREDGEfh_norm)
# Keep: mpa and spp; AIC = 449.6 (note: w/ lfm not sig. worse)
# Time to ignition
hpDREDGEtti_norm <- dredge(hpMEMtti_norm)
head(hpDREDGEtti_norm)
# Keep: mpa and spp; AIC = 693.2
# Flame duration
hpDREDGEfd_norm <- dredge(hpMEMfd_norm)
head(hpDREDGEfd_norm)
# Keep: mpa and spp; AIC = 521 (note: not sig. worse w/o mpa)
# Glow to ignition
hpDREDGEgti_norm <- dredge(hpMEMgti_norm)
head(hpDREDGEgti_norm)
# Keep: mpa and spp' AIC = 661.8 (note: not sig. worse w/o mpa)
# Time to first glow
hpDREDGEttfg_norm <- dredge(hpMEMttfg_norm)
head(hpDREDGEttfg_norm)
# Keep: mpa and spp; AIC = 700.9
# Temp max
hpDREDGEtemp_max_norm <- dredge(hpMEMtemp_max_norm)
head(hpDREDGEtemp_max_norm)
# Keep: lfm, mpa and spp; AIC = 834.7 (not sig. worse w/o mpa)
# Glow duration
hpDREDGEgd_norm <- dredge(hpMEMgd_norm)
head(hpDREDGEgd_norm)
# Keep: mpa and spp; AIC = 760.8
```

## Epiradiator

### No data manipulation

#### Maximal model
```{r}
epiMEMfh <- lmer(data = vd_main_df, subset = model == "EPI", fh ~ mpa + spp + sample_wt + lfm_outliers_out + (1|precip_2mo) + (1|location) + (1|individual)) # precip_2mo is a time proxy that represents the amount of precipitation over the past two months

epiMEMtti <- lmer(data = vd_main_df, subset = model == "EPI", tti ~ mpa + spp + sample_wt + lfm_outliers_out + (1|precip_2mo) + (1|location) + (1|individual))

epiMEMfd <- lmer(data = vd_main_df, subset = model == "EPI", fd ~ mpa + spp + sample_wt + lfm_outliers_out + (1|precip_2mo) + (1|location) + (1|individual))

epiMEMgti <- lmer(data = vd_main_df, subset = model == "EPI", gti ~ mpa + spp + sample_wt + lfm_outliers_out + (1|precip_2mo) + (1|location) + (1|individual))

epiMEMttfg <- lmer(data = vd_main_df, subset = model == "EPI", ttfg ~ mpa + spp + sample_wt + lfm_outliers_out + (1|precip_2mo) + (1|location) + (1|individual))

epiMEMtemp_max <- lmer(data = vd_main_df, subset = model == "EPI", temp_max ~ mpa + spp + sample_wt + lfm_outliers_out + (1|precip_2mo) + (1|location) + (1|individual))

epiMEMgd <- lmer(data = vd_main_df, subset = model == "EPI", gd ~ mpa + spp + sample_wt + lfm_outliers_out + (1|precip_2mo) + (1|location) + (1|individual))
```

#### Dredging
```{r}
options(na.action = "na.fail")
# Flame height
epiDREDGEfh <- dredge(epiMEMfh)
head(epiDREDGEfh)
## Keep: sample.wt, mpa and spp; AIC = 545.5
# Time to ignition
epiDREDGEtti <- dredge(epiMEMtti)
head(epiDREDGEtti)
## Keep: sample.wt, mpa and spp; AIC = 677.7
# Flame duration
epiDREDGEfd <- dredge(epiMEMfd)
head(epiDREDGEfd)
## Keep: sample.wt and spp; AIC = 537.1
# Glow to ignition
epiDREDGEgti <- dredge(epiMEMgti)
head(epiDREDGEgti)
## Keep: sample weight, mpa and spp; AIC = 686.4
# Time to first glow
epiDREDGEttfg <- dredge(epiMEMttfg)
head(epiDREDGEttfg)
## Keep: sample weight and spp; AIC = 611.8 (with mpa, not sig. worse)
# Temp max
epiDREDGEtemp_max <- dredge(epiMEMtemp_max)
head(epiDREDGEtemp_max)
## Keep: sample weight, mpa, lfm and spp; AIC = 921.9 (w/o lfm, not sig. worse)
# Glow duration
epiDREDGEgd <- dredge(epiMEMgd)
head(epiDREDGEgd)
## Keep: sample weight, mpa and spp; AIC = 898.6 (w/o mpa, not sig. worse)
```

### Dry Weight and Water Weight
#### Models
```{r}
epiMEMfh2 <- lmer(data = vd_main_df, subset = model == "EPI", fh ~ mpa + spp + dry_wt + water_wt + (1|precip_2mo) + (1|location) + (1|individual)) # precip_2mo is a time proxy that represents the amount of precipitation over the past two months

epiMEMtti2 <- lmer(data = vd_main_df, subset = model == "EPI", tti ~ mpa + spp + dry_wt + water_wt + (1|precip_2mo) + (1|location) + (1|individual))

epiMEMfd2 <- lmer(data = vd_main_df, subset = model == "EPI", fd ~ mpa + spp + dry_wt + water_wt + (1|precip_2mo) + (1|location) + (1|individual))

epiMEMgti2 <- lmer(data = vd_main_df, subset = model == "EPI", gti ~ mpa + spp + dry_wt + water_wt + (1|precip_2mo) + (1|location) + (1|individual))

epiMEMttfg2 <- lmer(data = vd_main_df, subset = model == "EPI", ttfg ~ mpa + spp + dry_wt + water_wt + (1|precip_2mo) + (1|location) + (1|individual))

epiMEMtemp_max2 <- lmer(data = vd_main_df, subset = model == "EPI", temp_max ~ mpa + spp + dry_wt + water_wt + (1|precip_2mo) + (1|location) + (1|individual))

epiMEMgd2 <- lmer(data = vd_main_df, subset = model == "EPI", gd ~ mpa + spp + dry_wt + water_wt + (1|precip_2mo) + (1|location) + (1|individual))
```

#### Dredging
```{r}
#options(na.action = "na.fail") If errors pop up, run this line and try again before troubleshooting further
# Flame height
epiDREDGEfh2 <- dredge(epiMEMfh2)
head(epiDREDGEfh2)
## Keep: water_wt, dry_wt, spp; AIC = 538.3 (note: not sig. worse with mpa)
# Time to ignition
epiDREDGEtti2 <- dredge(epiMEMtti2)
head(epiDREDGEtti2)
## Keep: water_wt, dry_wt, mpa and spp (all variables); AIC = 669.9
# Flame duration
epiDREDGEfd2 <- dredge(epiMEMfd2)
head(epiDREDGEfd2)
## Keep: water_wt, dry_wt, mpa and spp (all variables);  AIC = 532.4 (w/o mpa not sig. worse)
# Glow to ignition
epiDREDGEgti2 <- dredge(epiMEMgti2)
head(epiDREDGEgti2)
## Keep: water_wt, dry_wt, mpa and spp (all variables); AIC = 675.9
# Time to first glow
epiDREDGEttfg2 <- dredge(epiMEMttfg2)
head(epiDREDGEttfg2)
## Keep: water_wt, dry_wt and spp; AIC = 603.5
# Temp max
epiDREDGEtemp_max2 <- dredge(epiMEMtemp_max2)
head(epiDREDGEtemp_max2)
## Keep: water_wt, dry_wt, mpa and spp (all variables); AIC = 908.5
# Glow duration
epiDREDGEgd2 <- dredge(epiMEMgd2)
head(epiDREDGEgd2)
## Keep: water_wt, dry_wt, mpa and spp (all variables); AIC = 888.9 (w/o mpa not sig. worse)
```
Take-aways: Again -- like the hot plate -- both dry weight and water weight play a role. In the epiradiator, mpa is a chosen predictor in the model selection process for 5/7 of the flam. metrics vs. 4/7 in the hot plate.

### Normalized
#### Models
```{r}
epiMEMfh_norm <- lmer(data = vd_main_df, subset = model == "EPI", fh_norm ~ mpa + spp + lfm_outliers_out + (1|precip_2mo) + (1|location) + (1|individual))

epiMEMtti_norm <- lmer(data = vd_main_df, subset = model == "EPI", tti_norm ~ mpa + spp + lfm_outliers_out + (1|precip_2mo) + (1|location) + (1|individual))

epiMEMfd_norm <- lmer(data = vd_main_df, subset = model == "EPI", fd_norm ~ mpa + spp + lfm_outliers_out + (1|precip_2mo) + (1|location) + (1|individual))

epiMEMgti_norm <- lmer(data = vd_main_df, subset = model == "EPI", gti_norm ~ mpa + spp + lfm_outliers_out + (1|precip_2mo) + (1|location) + (1|individual))

epiMEMttfg_norm <- lmer(data = vd_main_df, subset = model == "EPI", ttfg_norm ~ mpa + spp + lfm_outliers_out + (1|precip_2mo) + (1|location) + (1|individual))

epiMEMtemp_max_norm <- lmer(data = vd_main_df, subset = model == "EPI", temp_max_norm ~ mpa + spp + lfm_outliers_out + (1|precip_2mo) + (1|location) + (1|individual))

epiMEMgd_norm <- lmer(data = vd_main_df, subset = model == "EPI", gd_norm ~ mpa + spp + lfm_outliers_out + (1|precip_2mo) + (1|location) + (1|individual))
```

#### Dredging
```{r}
# Flame height
epiDREDGEfh_norm <- dredge(epiMEMfh_norm)
head(epiDREDGEfh_norm)
# Keep: mpa and spp; AIC = 674.3
# Time to ignition
epiDREDGEtti_norm <- dredge(epiMEMtti_norm)
head(epiDREDGEtti_norm)
# Keep: mpa and spp; AIC = 808.5
# Flame duration
epiDREDGEfd_norm <- dredge(epiMEMfd_norm)
head(epiDREDGEfd_norm)
# Keep: spp; AIC = 661.3 (w/ mpa not sig. worse)
# Glow to ignition
epiDREDGEgti_norm <- dredge(epiMEMgti_norm)
head(epiDREDGEgti_norm)
# Keep: mpa and spp; AIC = 819.5 (not sig. worse with lfm)
# Time to first glow
epiDREDGEttfg_norm <- dredge(epiMEMttfg_norm)
head(epiDREDGEttfg_norm)
# Keep: mpa and spp; AIC = 731.4 (w/o mpa not sig. worse)
# Temp max
epiDREDGEtemp_max_norm <- dredge(epiMEMtemp_max_norm)
head(epiDREDGEtemp_max_norm)
# Keep: lfm, mpa and spp; AIC = 1111.7 (w/o lfm not sig. worse)
# Glow duration
epiDREDGEgd_norm <- dredge(epiMEMgd_norm)
head(epiDREDGEgd_norm)
# Keep: mpa and spp; AIC = 1025.8
```

Setting na.action back to default
```{r}
options(na.action = "na.omit")
```

# AIC Dataframe
```{r}
flam.metric <- c(rep(c("Flame Height", "Time to Ignition", "Flame Duration", "Glow to Ignition", "Time to First Glow", "Maximum Temperature", "Glow Duration"), 2))
model <- c(rep("HP", 7), rep ("EPI", 7))
aic.no.manipulation <- c(487.4, 740.3, 581.5, 751.9, 757.2, 749.9, 868.3, 545.5, 677.7, 527.1, 686.4, 611.8, 921.9, 898.6)
aic.dry.wt.water.wt <- c(482.4, 734.5, 577.8, 745.8, 750.7, 743, 861.8, 538.3, 669.9, 532.4, 675.9, 603.5, 908.5, 888.9)
aic.normalized <- c(449.6, 693.2, 521, 661.8, 700.9, 834.7, 760.8, 674.3, 808.5, 661.3, 819.5, 731.4, 1111.7, 1025.8)

aic.df <- data.frame(flam.metric, model, aic.no.manipulation, aic.dry.wt.water.wt, aic.normalized)
```


# Conclusions of Model Selection
Since we will be using the mixed effects models in the water content vs. flam. graphs as well as the variance decomposition, we may want to select slightly different models for each. 

For the variance decomposition, the most common explanatory variables should be chosen for ALL of the mixed effect models. Secondly, since sample weight was significant in all of the models when there was no data manipulation of the flam. metrics, it makes sense to me to normalize the flam. metrics prior to running the mixed effects models in effort to account for the variability in sample weight and its effects on the flammability metrics. This will also simplify the variance decomposition by only having two explanatory variables of interest for both models.

The mixed effects models will have the following fixed effects: water potential (mpa) and species (spp)

After running the mixed effects models with the wet weight and the dry weight separated, I think it might be a good idea to try the variance decomposition process with the maximal models as well.
      --            --            --            --            --            --
For the water content/status vs. flam. graphs, it makes sense to use the models that were "best suited" (note: there is a caveat here that since we will be visualizing water status or water content vs. the flam. metrics, water status (mpa) or water content (lfm) should ALWAYS be included in the model regardless of if they were selected for in the model selection process) for each individual flam. metric since we are not comparing all of the flam. metrics to each other at one time. Instead, each graph will have the flam. metric vs. the water status or content. Since we are interested in the actual flam. metric in these cases, we should not use the normalized values as those would be difficult to interpret. Therefore, the mixed effects models utilized for each chamber design and each flam. metric will vary depending on the above model selection process.