---
title: "Metadata"
author: "Joe Celebrezze"
date: "2023-01-13"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(here)
here = here::here
library(tidyverse)
```

This .Rmd file covers the necessary metadata for the datasets that we used in the analyses for this manuscript.

# --------------------------

# Raw Data

## lit.review.csv
```{r}
lit.review <- read_csv(here("raw-data", "lit.review.csv"))
head(lit.review)
```

*author*: author(s) of the given study, et al denotes that there were more than two authors, in which the first author was named prior to et al

*year*: publishing year of the given study

*sample.size.description*: notes taken on the sample size used in the flammability tests; if NA, then no information was provided; this was used to inform the next four columns

*sample.weight*: average weight of flammability samples in grams; if NA, then no information was provided

*sample.length.cm*: average length of flammability samples in cm; if NA, then no information was provided

*sample.area.cm*: average area of flammability samples in cm^2; if NA, then no information was provided

*sample.volume.cm*: average volume of flammability samples in cm^3; if NA, then no information was provided

**Methods Columns**: the following 16 columns -- *epiradiator*, *wind.tunnel*, *muffle.furnace*, *MLC*, *xylene.lattice*, *fire.bench*, *grill*, *oxygen.bomb.calorimeter*, *steel.ring.litter.bed*, *tray*, *FFB*, *FPA*, *cone.calorimeter*, *bunsen.burner*, *other*, *intermediate.scale.calorimeter* -- were formatted in the same way where they were given a binary identifier of 1 or 0, 1 denoting that the study used this specific method and 0 denoting that thy did not. The dataset was organized so that there was only 1 method used per row, so in cases where multiple methods were used by one study, then multiple rows were assigned for methods characterization (see *duplicate*). For in-depth descriptions of methods, see the table located in the appendix (Table A1).

*duplicate*: assigned a binary identifier of N (no) or Y (yes) denoting whether or not multple methods were used in the same study

*model*: a character vector assigned to the method used in the row where the following abbreviations were used matching up to the list of columns above in **Methods Columns** -- EPI, WT, MF, MLC, XL, FB, grill, OB, SR, tray, FFB, FPA, CC, BB, other, ISC

*notes*: any extra notes taken on the methods used in the study -- often for somewhat unique changes to methods or for 'other' methods

## lit.review.locations.csv
```{r}
lit.review.locations <- read_csv(here("raw-data", "lit.review.locations.csv"))
head(lit.review.locations)
```

*study*: identifier of the study using the author(s) and publishing year, NA values are for instances where multiplee locations were provided for the same study, in which the numerical id (see below) can adequately cross-reference the location data to the correct study

*id*: numerical identifier of the study, where the studies were ordered in alphabetical order of the last name of the first author. There are certain gaps in id's for instances where studies did not include any information on locations

*latitude*: latitude of the study location in decimal degrees (DD)

*longitude*: longitude of the study location in decimal degrees (DD)

*location notes*: notes taken on the study location(s). This can give a sense of whether or not the latitude and longitude reported are specific or if they are relatively broad.

## local_flam_data_all.csv
```{r}
local_flam_data_all <- read_csv(here("raw-data", "local_flam_data_all.csv"))
head(local_flam_data_all)
```

*individual*: an identifier for the individual which includes the date (YYYY_month), species (CEME = *Ceanothus megacarpus* and ADFA = *Adenostoma fasciculatum*) and a identification number for the individual

*sample*: the identification number for the individual

*round*: this describes the order in which the samples were burned over the course of a laboratory drydown (i.e., round = 1 means the first sample of that particular individual that we burned)

*spp*: an abbreviation for the species tested (CEME = *Ceanothus megacarpus* and ADFA = *Adenostoma fasciculatum*)

*model*: an identifier of the method used (EPI = epiradiator and HP = hot plate)

*mpa*: water potential (-MPa), reported here as a positive number but changed to negative values in the data wrangling step

*lfm*: live fuel moisture (LFM, %), as measured using the following equation, taken on a subsample directly before testing flammability
\start{equation}
LFM = 100 \times \frac{fresh weight - dry weight}{dry weight}
\end{equation}

*lfm_notes*: any notes taken on the live fuel moisture sample

*fh*: the maximum flame height (cm) observed during combustion

*ttfg*: time to first glow (seconds); time elapsed between loading the sample into the flammability chamber and the beginning of the glow time

*gti*: glow to ignition (seconds); time elapsed between beginning of glow time and the time which ignition occurred

*tti*: time to ignition (seconds); time elapsed between loading the sample into the flammability chamber and the time which ignition occurred

*fd*: flame duration (seconds); duration of the combustion from ignition to extinction of the flame

*gd*: glow duration (seconds); time elapsed between beginning and end of glow time

*pfg*: post-flame glow (seconds); time elapsed between extinction of flame (end of comubstion) and end of glow time

*ignition*: binary identifier describing whether or not the sample ignited (1 = ignited, 0 = not ignited)

*start_temp*: starting temperature (degrees Celsius)...

*temp_max*: maximum temperature (degrees Celsius)...

*ignition_temp*: temperature (degrees Celsius) at the point of ignition

*prop_new*: estimated proportion of new growth in the sample as observed directly prior to loaading the sample in the flammability chamber

*sample_wt*: weight (g) of the sample loaded into the flammability chamber

*glow*: binary identifier describing whether or not the sample glowed (1 = glowed, 0 = did not glow)

*year_month*: identifier of date when we ran flammability tests in format YYYY_Month (e.g., 2023_January)

*year*: identifier of year when we ran flammability tests in format YYYY

*month*: identifier of month, written out with a capital letter to start, when we ran flammability tests

*dry_wt*: the weight (g) after oven-drying for 24hr at 100C from the subsample used to measure live fuel moisture

*fresh_wt*: the weight (g) of the subsample used to measure live fuel moisture prior to oven-drying

*water_wt*: the difference between the *fresh_wt* and the *dry_wt* representing the weight of water (g) in the LFM subsample

*site*: a character identifier describing the site that we gathered the samples from (either St. Marys = chapparal Site 1 = 34.4613N, -119.6934W or Painted Caves = chapparal Site 2 = 34.4931N, -119.7910W)

*lfm_outliers_out*: a column reporting LFM values, with outliers replaced with NAs

*lfm_n_as_imputed*: a column reporting LFM values, with NAs replaced by imputing the predicted LFM value at that water potential

*gr*: represents the 10% bin of LFM that the sample fell into (e.g., (90,100] = the sample's LFM was greater than 90% and less than or equal to 100%)

*precip_2month*: month used when accessing precipitation data (essentially a duplicate column of year_month)

*precip_2mo*: the precipitation recorded by a weather station at Santa Barbara Botanical Gardens for the 2 months prior to flammability testing

*season*: an identifier of whether or not sampling efforts occurred after (season = Wet) the beginning of seasonal rains (typically in the late fall to spring) or before (season = Dry) seasonal rains (typically late spring or early summer to late fall)

*hydration*: an identifier denoting the hydration status of the sample based on LFM, split into "dry" (0-60% LFM), "moderate" (60-90% LFM), and "hydrated" (>90% LFM)

*bins5lfm*: represents the 5% bin of LFM that the sample fell into

*bins10lfm*: duplicate column of *gr*

*bins20lfm*: represents the 20% bin of LFM that the sample fell into

*temp_change*: the difference in temperature (degrees C) from the starting temperature to the maximum temperature (i.e., *temp_max* - *start_temp*)

*gdw_gfw*: grams of dry weight per grams of fresh weight (from LFM subsample); used in calculation of *dw.flam.sample* (see below)

*gww_gdw*: grams of wet weight per grams of dry weight (from LFM subsample); not used in analyses

*flam_index*: derived from Essaghi et. al. 2017, using maximum *tti* and maximum *fh*, an index of flammability as a scale of least (1) to most (20) flammable. The following equation was used: 
\begin{equation}
flam.index = 9.1 \times \frac{25 \times tti}{(12.5 + tti)^\frac{fh}{fh + 5.5}} 
\end{equation}

*max_mpa_sample*: the maximum (wettest) water potential measured using this method

## SEKI_flammability.csv
```{r}
SEKI_flammability <- read_csv(here("raw-data", "SEKI_flammability.csv"))
head(SEKI_flammability)
```

Many of the following columns are identical to the columns described above, so I will only be providing extra information as necessary, otherwise, see the column descriptions for local_flam_data_all.csv

*sample*: an identifier of the individual using the following format, site.individual (i.e., 2.1 = site 2, individual 1 (at that site))

*round*: see above

*spp*: abbreviations of study species as follows: ARPA = *Arctostaphylos patula*, ABCO = *Abies concolor*, CADE = *Calocedrus decurrens*, CECO = *Ceanothus cordulatus*, PIJE = *Pinus jeffreyii*, and QUKE = *Quercus kelloggii*; note that only ARPA and CECO were seriously considered in this study due to the other four species having very few ignitions (primarily due to our epiradiator breaking during testing, rather than a low ignition percentage)

*model*: see above

*mpa*: water potential (MPa) as a negative value (which is the correct representation of water potential)

*lfm*: see above

*lfm.notes*: see above lfm_notes

**Flammability Metrics**: *fh*, *ttfg*, *gti*, *tti*, *fd*, *gd*, *pfg*, *start.temp* (see *start_temp*), *temp.max* (see *temp_max*), *ignition.temp* (see *ignition_temp*), *prop.new* (see *prop_new*), *sample.wt* (see *sample_wt*), and *glow* are all identical to what was reported above for local_flam_data_all.csv

*ignition*: mostly identical to what was reported above, but in some cases, when the sample ignited more than once, a '2' is reported, making it no longer a binary identifier

*year* and *month*: see above

*dry.wt*, *fresh.wt*, and *water.wt*: see *dry_wt*, *fresh_wt* and *water_wt* above and note *bottle.wt* below

*site*: numerical identifier of sampling site (input coordinates here!)

*bottle.wt*: the weight of the tin (g) in which we weighed all measurements for LFM measurements. Note that the *dry.wt* and *fresh.wt* columns include the weight of the tin as well as the weight of the sample in every case which differs from local_flam_data_all where the *dry_wt* and *fresh_wt* have the bottle subtracted from the weight

*ttms*: time elapsed from beginning of ignition to the point where the entire sample is engulfed in flames (seconds); note that we did not end up using this, as -- especially for the epiradiator burns -- we deemed it to be too subjective and inconsistent of a metric to reliably use in analyses

## pv_summary_df_timing.csv
```{r}
pv_summary_df_timing <- read_csv(here("raw-data", "pv_summary_df_timing.csv"))
head(pv_summary_df_timing)
```

Although we did not end up using pressure-volume curve data in any of the analyses reported in the paper or the supplementary index, we did use it in some exploratory/extra analyses looking at whether or not we could detect thresholds in flammability metrics at or around the identified turgor loss point for species; therefore, it is in the GitHub repository.

Pressure-volume curves (PV curves) were conducted using the protocols outlined in Tyree & Hammel 1972 as described below (adapted from Boving et. al., *in review*):

20-40 cm samples were collected from the 6 individuals from Site 1 (for either chaparral or SEKI species) shortly after dawn by cutting from terminal shoots. Then they were sealed in moistened plastic bags and transported to the laboratory in a cooler. Samples were either immediately processed within 1 hour of sample collection (which was more plausible for the chaparral species) or stored in a refrigerator at 4C between processing (maximally 12 hours after collection).

Prior to running the PV curves, we cut branches incrementally underwater into smaller branchlets and rehydrated them in cool darkness for 2-4 hours, after which we removed healthy leaves or small leafy shoots from the branch using a razor blade. To avoid the effects of oversaturation, leaves and stems that had been underwater during rehydration were typically avoided during PV curve analysis. For *Pinus jeffreyi*, however, fascicles were rehydrated by placing the entire excised fascicle in water making the avoidance of using leaves that were underwater during rehydration impossible.

To run the PV curves, we measured leaf weight (to 0.0001 g) and then rapidly measured water potential (MPa) for 3-6 rehydrated leaves or branchlets (1 per individual). While measuring water potential, care was taken to slowly increase pressure (0.1 Mpa/sec) for accurate water potential estimates, as well as slowly remove pressure from the tank following measurements avoiding rapid cooling of the sample. Throughout the PV curves, a plot was made using -1/MPa and sample weight; this informed when we had reached the TLP (at the intersection of the linear portion of the curve and the exponential portion), and we ceased measurements after three to five datapoints in the linear section of the curve. 

Afterwards, we determined saturated water content (SWC) by extrapolating a plot of water potential vs. water weight to water potential = 0, which was used to determine relative water content (RWC) and LFM using Eq. 1. The LFM, RWC, and water potential at TLP corresponded with the point at which the exponential section of the curve met the linear section, determined by maximizing the linear fit (R2) of the tail of the curve. The osmotic potential at full turgor was calculated as the y-intercept of the linear section of the curve. PV parameters were determined using the protocols available on Prometheus wiki (Sack et. al.; url: https://prometheusprotocols.net/function/water-relations/pressure-volume-curves/leaf-pressure-volume-curve-parameters/).

These are the columns included in this dataset:

*spp*: a species identifier following these abbreviations: ARPA = *Arctostaphylos patula*, ABCO = *Abies concolor*, CADE = *Calocedrus decurrens*, CECO = *Ceanothus cordulatus*, PIJE = *Pinus jeffreyii*, QUKE = *Quercus kelloggii*, CEME = *Ceanothus megacarpus*, and ADFA = *Adenostoma fasciculatum*

*timing*: the season that the PV curves were completed

*mean_tlp*: the average of the turgor loss point (TLP) across individuals tested (MPa)

*lwr*: the lower bounds of the TLP (MPa) as identified using...

*upr*: the upper bounds of the TLP (MPa) as identified using..

*mean_lfm*: the average of the TLP across individuals tested expressed as live fuel moisture (%); note that we did not do this for spring PV curves

*lwr_lfm*: the lower bounds of the TLP (LFM, %) as identified using...

*upr_lfm*: the upper bounds of the TLP (LFM, %) as identified using..

# --------------------------

# Processed Data

## seki_flam_data_all.csv
```{r}
seki_flam_data_all <- read_csv(here("processed-data", "seki_flam_data_all.csv"))
head(seki_flam_data_all)
```

*model.spp.gr.sample*: an identifier that includes *year_month*, *model*, *spp*, *gr*, and *sample* in that order, with underscores between each variable

*ignition_no_double*: after removing non-ignitions, all instances where *ignition* = 2 (multiple ignitions), are coded as NA. Otherwise, *ignition_no_double* = 1

*ros*: a metric derived from this equation: 10 / *fd* to represent rate of spread (cm/second); not used in any analyses

*gdw.gfw*: grams of dry weight per grams of fresh weight (using measurements taken for LFM subsample); not used in analyses, but used to calculate *dw.flam.sample*

*max.mpa.sample*: the highest (wettest) water potential that the individual reached throughout the laboratory benchtop drydown

*flam.index*: see flam_index in local_flam_all.csv

*mean.wt*: the mean sample weight (*sample.wt*) calculated for each species for either *model* (e.g., *mean.wt* for *Abies concolor* for the epiradiator method)

*dw.flam.sample*: an estimate of the dry weight in the sample loaded into the flammability chamber derived from the *sample.wt* and the metrics that were used to calculate live fuel moisture (of a subsample collected at the same time as the flammability sample) (*dry.wt* and *fresh.wt*); this was used extensively in analyses and was calculated using this equation
\begin{equation}
sample.wt \times \frac{dry.wt}{fresh.wt}
\end{equation}
or
\begin{equation}
sample.wt \times gdw.gfw
\end{equation}

*ww.flam.sample*: an estimated of the water weight in the sample loaded into the flammability chamber; this was used often in analyses and was calculated using this equation 
\begin{equation}
sample.wt - dw.flam.sample
\end{equation}

*dry.norm...*: the seven columns -- *dry.norm.fh*, *dry.norm.gd*, *dry.norm.fd*, *dry.norm.pfg*, *dry.norm.ttfg*, *dry.norm.tti*, *dry.norm.gti* -- are the flammability metrics normalized by the dry weight of the flammability sample, as reported in *dw.flam.sample*; these were used in some exploratory analyses, but not very extensively

## Combined Datasets
The following datasets were in 1.data_wrangling_methods.Rmd as a combination of local_flam_data_all.csv and seki_flam_data_all.csv and vary in the amount of data they include. In most cases, they have the same columns as defined previously in local_flam_data_all.csv and seki_flam_data_all.csv. All extra columns are defined as necessary. One recurring column was:

*location*: either local (chapparal sites) or seki (Sierra Nevadas sites, seki = Sequoia-Kings Canyon)

The first two we used most often (by far), while the last three were used primarily for extra analyses or exploratory analyses

### bothmethods_bothlocations_wide.csv
```{r}
bothmethods_bothlocations_wide <- read_csv(here("processed-data", "bothmethods_bothlocations_wide.csv"))
head(bothmethods_bothlocations_wide)
```

This combines the data gathered from the SEKI and chapparal sites, from both epiradiator and hot plate methods. In this .csv, the data is in a 'wide' format with columns for the data from the epiradiator (_epi) and the hot plate (_hp). This was a possibility due to us simultaneously burning plant samples using both methods, so for each individual and round, there was data for both epiradiator and hot plate methods

### bothmethods_bothlocations_long.csv
```{r}
bothmethods_bothlocations_long <- read_csv(here("processed-data", "bothmethods_bothlocations_long.csv"))
head(bothmethods_bothlocations_long)
```

This combines the data gathered from the SEKI and chapparal sites, from both epiradiator and hot plate methods by stitching the rows together. Unlike the 'wide' format, there are individual rows for each burn that have a *model* column describing if it is from the epiradiator or hot plate method.

### bothm_bothl_manual_ignitions_in.csv
```{r}
bothm_bothl_manual_ignitions_in <- read_csv(here("processed-data", "bothm_bothl_manual_ignitions_in.csv"))
head(bothm_bothl_manual_ignitions_in)
```

This includes data-of-interest (excluding certain species as noted in 1.data_wrangling_methods.Rmd) for both methods and both locations and includes manual ignitions

### bothmethods_and_locations_long_noignitionsincluded.csv
```{r}
bothmethods_and_locations_long_noignitionsincluded <- read_csv(here("processed-data", "bothmethods_and_locations_long_noignitionsincluded.csv"))
head(bothmethods_and_locations_long_noignitionsincluded)
```
This includes non-ignitions; the columns have all been defined above.

### bothmethods_and_locations_wide_noignitionsincluded.csv
```{r}
bothmethods_and_locations_wide_noignitionsincluded <- read_csv(here("processed-data", "bothmethods_and_locations_wide_noignitionsincluded.csv"))
head(bothmethods_and_locations_wide_noignitionsincluded)
```
This includes non-ignitions but in a wide format with variables followed by _epi or _hp depending on which *model* was used
