---
title: "1:1, Variance Comparisons - Methods Paper"
author: "Joe Celebrezze"
date: "12/16/2021"
output:
  html_document:
    toc: true
    toc_depth: 4
    theme: united
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Loading in necessary packages
```{r, include = FALSE}
library(tidyverse)
select = dplyr::select
library(here)
here = here::here
library(ggpubr) #to put graphs side by side
library(cowplot) #to put graphs side by side
library(gtsummary) #for statistical summary tables
library(vars) #for variance decomposition
library(lme4) #for mixed effects models
library(reshape2) #for "melting" dataframe into longer form (variance decomposition)
#Add in packages as necessary so no redundant packages
```

# Loading in datasets
```{r, include = FALSE}
main_df <- read_csv(here("processed-data/compiled-datasets/METHODS/bothmethods_bothlocations_long.csv"))
wide_df <- read_csv(here("processed-data/compiled-datasets/METHODS/bothmethods_bothlocations_wide.csv"))
```

# ---------------------------------

# Try 1

# First, 1:1 graphs
These graphs show the flam. metrics for the EPI and the flam. metrics for the HP on a scatterplot; if there were no major differences between the two methods, the points would land squarely on the 1:1 line

## Getting dataset all prepped, centered and scaled
```{r}
df1 <- wide_df %>% 
  select(temp_max_epi, temp_max_hp, ignition_temp_epi, ignition_temp_hp, fh_epi, fh_hp, fd_epi, fd_hp, ttfg_epi, ttfg_hp, gti_epi, gti_hp, tti_epi, tti_hp, gd_epi, gd_hp, pfg_epi, pfg_hp, spp_epi, hydration_epi, mpa_epi) %>% 
  na.omit() %>% 
  mutate(fh_epi = fh_epi - mean(fh_epi), fh_hp = fh_hp - mean(fh_hp),
        fd_epi = fd_epi - mean(fd_epi), fd_hp = fd_hp - mean(fd_hp),
        temp_max_epi = temp_max_epi - mean(temp_max_epi),
        temp_max_hp = temp_max_hp - mean(temp_max_hp),
        ignition_temp_epi = ignition_temp_epi - mean(ignition_temp_epi),
        ignition_temp_hp = ignition_temp_hp - mean(ignition_temp_hp),
        ttfg_epi = ttfg_epi - mean(ttfg_epi), ttfg_hp = ttfg_hp - mean(ttfg_hp),
        gti_epi = gti_epi - mean(gti_epi), gti_hp = gti_hp - mean(gti_hp),
        tti_epi = tti_epi - mean(tti_epi), tti_hp = tti_hp - mean(tti_hp),
        gd_epi = gd_epi - mean(gd_epi), gd_hp = gd_hp - mean(gd_hp), 
        pfg_epi = pfg_epi - mean(pfg_epi), pfg_hp = pfg_hp - mean(pfg_hp)) %>%  #centered variables of interest
  mutate(fh_epi = scale(fh_epi), fh_hp = scale(fh_hp), fd_epi = scale(fd_epi), fd_hp = scale(fd_hp), ttfg_epi = scale(ttfg_epi), ttfg_hp = scale(ttfg_hp), tti_epi = scale(tti_epi), tti_hp = scale(tti_hp), gti_epi = scale(gti_epi), gti_hp = scale(gti_hp), gd_epi = scale(gd_epi), gd_hp = scale(gd_hp), pfg_epi = scale(pfg_epi), pfg_hp = scale(pfg_hp), ignition_temp_epi = scale(ignition_temp_epi), ignition_temp_hp = scale(ignition_temp_hp), temp_max_epi = scale(temp_max_epi), temp_max_hp = scale(temp_max_hp))#scaled variables of interest  
```

## 1:1 Graphs!
```{r}
tti.plot <- ggplot(df1, aes(x = tti_epi, y = tti_hp, color = spp_epi)) +
  ylim(-2, 3.5) +
  xlim(-2, 3.5) +
  geom_point() +
  geom_abline() +
  theme_bw() +
  coord_equal()+
  labs(x = "Time to Ignition (Epiradiator)", y = "Time to Ignition (Hot Plate)", color = "Species") +
  theme_bw() + theme(axis.text = element_blank(),
                     aspect.ratio = 1/1)

fh.plot <- ggplot(df1, aes(x = fh_epi, y = fh_hp, color = spp_epi)) +
  ylim(-3, 3) +
  xlim(-3, 3) +
  geom_point() +
  geom_abline() +
  theme_bw()+
  coord_equal() +
  labs(x = "Flame Height (Epiradiator)", y = "Flame Height (Hot Plate)", 
       color = "Species") +
  theme_bw() + theme(axis.text = element_blank(),
                     aspect.ratio = 1/1)

fd.plot <- ggplot(df1, aes(x = fd_epi, y = fd_hp, color = spp_epi)) +  
  ylim(-2, 3.5) +
  xlim(-2, 3.5) +
  geom_point() +
  geom_abline() +
  theme_bw()+
  coord_equal() +
  labs(x = "Flame Duration (Epiradiator)", y = "Flame Duration (Hot Plate)", color = "Species") +
  theme_bw() + theme(axis.text = element_blank(),
                     aspect.ratio = 1/1)
  
gd.plot <- ggplot(df1, aes(x = gd_epi, y = gd_hp, color = spp_epi)) +
  ylim(-2.5, 3.5) +
  xlim(-2.5, 3.5) +
  geom_point() +
  geom_abline() +
  labs(x = "Glow Duration (Epiradiator)", y = "Glow Duration (Hot Plate)", color = "Species") +
  theme_bw() + theme(axis.text = element_blank(),
                     aspect.ratio = 1/1)
  
gti.plot <- ggplot(df1, aes(x = gti_epi, y = gti_hp, color = spp_epi)) +
  ylim(-2.5, 3.5) +
  xlim(-2.5, 3.5) +
  geom_point() +
  geom_abline() +
  labs(x = "Glow to Ignition (Epiradiator)", y = "Glow to Ignition (Hot Plate)", color = "Species") +
  theme_bw() + theme(axis.text = element_blank(),
                     aspect.ratio = 1/1)
  
# WHY DOES IT GO TO SIX
ttfg.plot <- ggplot(df1, aes(x = ttfg_epi, y = ttfg_hp, color = spp_epi)) +
  ylim(-2, 6) +
  xlim(-2, 6) +
  geom_point() +
  geom_abline() +
  labs(x = "Time to First Glow (Epiradiator)", y = "Time to First Glow (Hot Plate)", color = "Species") +
  theme_bw() + theme(axis.text = element_blank(),
                     aspect.ratio = 1/1)
  
temp.max.plot <- ggplot(df1, aes(x = temp_max_epi, y = temp_max_hp, color = spp_epi)) +
  ylim(-3, 4) +
  xlim(-3, 4) +
  geom_point() +
  geom_abline() +
  labs(x = "Max Temp. (Epiradiator)", y = "Max Temp. (Hot Plate)", color = "Species") +
  theme_bw() + theme(axis.text = element_blank(),
                     aspect.ratio = 1/1)

pfg.plot <- ggplot(df1, aes(x = pfg_epi, y = pfg_hp, color = spp_epi)) +
  ylim(-2.5, 4) +
  xlim(-2.5, 4) +
  geom_point() +
  geom_abline() +
  labs(x = "Post-Flame Glow (Epiradiator)", y = "Post-Flame Glow (Hot Plate)", color = "Species") +
  theme_bw() + theme(axis.text = element_blank(),
                     aspect.ratio = 1/1)
pfg.plot
```



Putting above 7 plots all on one
```{r}
ggarrange(tti.plot, fh.plot, fd.plot, gd.plot, gti.plot, ttfg.plot, temp.max.plot, ncol = 4, nrow = 2, widths = c(1,1,1,1), heights = c(1,1), common.legend = TRUE)

ggsave("figures/1to1graphs.jpg", height = 7, width = 10)
```

# ---------------------------------
# Try 2
## Dataset Prepping
- Excluding manual ignitions (therefore, excluding all CECO, as all hot plate tests of CECO were manual ignitions)
- Scaling, centering after excluding manual ignitions
- Species labels -> full names
```{r}
df2 <- wide_df %>% 
  filter(spp_epi != "CECO") %>% 
  select(temp_max_epi, temp_max_hp, ignition_temp_epi, ignition_temp_hp, fh_epi, fh_hp, fd_epi, fd_hp, ttfg_epi, ttfg_hp, gti_epi, gti_hp, tti_epi, tti_hp, gd_epi, gd_hp, pfg_epi, pfg_hp, spp_epi, hydration_epi, mpa_epi) %>% 
  na.omit() %>% 
  mutate(fh_epi = fh_epi - mean(fh_epi), fh_hp = fh_hp - mean(fh_hp),
        fd_epi = fd_epi - mean(fd_epi), fd_hp = fd_hp - mean(fd_hp),
        temp_max_epi = temp_max_epi - mean(temp_max_epi),
        temp_max_hp = temp_max_hp - mean(temp_max_hp),
        ignition_temp_epi = ignition_temp_epi - mean(ignition_temp_epi),
        ignition_temp_hp = ignition_temp_hp - mean(ignition_temp_hp),
        ttfg_epi = ttfg_epi - mean(ttfg_epi), ttfg_hp = ttfg_hp - mean(ttfg_hp),
        gti_epi = gti_epi - mean(gti_epi), gti_hp = gti_hp - mean(gti_hp),
        tti_epi = tti_epi - mean(tti_epi), tti_hp = tti_hp - mean(tti_hp),
        gd_epi = gd_epi - mean(gd_epi), gd_hp = gd_hp - mean(gd_hp), 
        pfg_epi = pfg_epi - mean(pfg_epi), pfg_hp = pfg_hp - mean(pfg_hp)) %>%  #centered variables of interest
  mutate(fh_epi = scale(fh_epi), fh_hp = scale(fh_hp), fd_epi = scale(fd_epi), fd_hp = scale(fd_hp), ttfg_epi = scale(ttfg_epi), ttfg_hp = scale(ttfg_hp), tti_epi = scale(tti_epi), tti_hp = scale(tti_hp), gti_epi = scale(gti_epi), gti_hp = scale(gti_hp), gd_epi = scale(gd_epi), gd_hp = scale(gd_hp), pfg_epi = scale(pfg_epi), pfg_hp = scale(pfg_hp), ignition_temp_epi = scale(ignition_temp_epi), ignition_temp_hp = scale(ignition_temp_hp), temp_max_epi = scale(temp_max_epi), temp_max_hp = scale(temp_max_hp))#scaled variables of interest  
```

```{r}
df2 <- df2 %>% 
  mutate(Species = case_when(
    spp_epi == "ADFA" ~ "A. fasciculatum", 
    spp_epi == "CEME" ~ "C. megacarpus",
    spp_epi == "ARPA" ~ "A. patula"
  ))
```

## Visualization
```{r, fig.width = 3.5, fig.height = 2.5}
tti.plot <- ggplot(df2, aes(x = tti_epi, y = tti_hp, color = Species)) +
  ylim(-2.5, 4) +
  xlim(-2.5, 4) +
  geom_point() +
  geom_abline() +
  theme_bw() +
  coord_equal()+
  labs(x = "Time to Ignition (Epiradiator)", y = "Time to Ignition (Hot Plate)", color = "Species") +
  scale_color_manual(values = c("#FC5130","#F7B801","#5F758E")) +
  annotate('text', x = -2.25, y = 3.75, label = 'a', size = 10) +
  theme_bw() + theme(axis.text = element_blank(),
                     aspect.ratio = 1/1,
                     axis.title = element_text(face = 'bold', size = 10),
                     legend.text = element_text(face = 'italic', size = 12),
                     legend.title = element_text(face = 'bold', size = 14))
tti.plot

fh.plot <- ggplot(df2, aes(x = fh_epi, y = fh_hp, color = Species)) +
  ylim(-2.5, 4) +
  xlim(-2.5, 4) +
  geom_point() +
  geom_abline() +
  theme_bw()+
  coord_equal() +
  labs(x = "Flame Height (Epiradiator)", y = "Flame Height (Hot Plate)", 
       color = "Species") +
  scale_color_manual(values = c("#FC5130","#F7B801","#5F758E")) +
  annotate('text', x = -2.25, y = 3.75, label = 'c', size = 10) +
  theme_bw() + theme(axis.text = element_blank(),
                     aspect.ratio = 1/1,
                     axis.title = element_text(face = 'bold', size = 10),
                     legend.text = element_text(face = 'italic', size = 12),
                     legend.title = element_text(face = 'bold', size = 14))
fh.plot

fd.plot <- ggplot(df2, aes(x = fd_epi, y = fd_hp, color = Species)) +  
  ylim(-2.5, 4) +
  xlim(-2.5, 4) +
  geom_point() +
  geom_abline() +
  theme_bw()+
  coord_equal() +
  labs(x = "Flame Duration (Epiradiator)", y = "Flame Duration (Hot Plate)", color = "Species") +
  scale_color_manual(values = c("#FC5130","#F7B801","#5F758E")) +
  annotate('text', x = -2.25, y = 3.75, label = 'b', size = 10) +
  theme_bw() + theme(axis.text = element_blank(),
                     aspect.ratio = 1/1,
                     axis.title = element_text(face = 'bold', size = 10),
                     legend.text = element_text(face = 'italic', size = 12),
                     legend.title = element_text(face = 'bold', size = 14))
fd.plot

gd.plot <- ggplot(df2, aes(x = gd_epi, y = gd_hp, color = Species)) +
  ylim(-2.5, 4) +
  xlim(-2.5, 4) +
  geom_point() +
  geom_abline() +
  labs(x = "Glow Duration (Epiradiator)", y = "Glow Duration (Hot Plate)", color = "Species") +
  scale_color_manual(values = c("#FC5130","#F7B801","#5F758E")) +
  annotate('text', x = -2.25, y = 3.75, label = 'f', size = 10) +
  theme_bw() + theme(axis.text = element_blank(),
                     aspect.ratio = 1/1,
                     axis.title = element_text(face = 'bold', size = 10),
                     legend.text = element_text(face = 'italic', size = 12),
                     legend.title = element_text(face = 'bold', size = 14))
gd.plot

gti.plot <- ggplot(df2, aes(x = gti_epi, y = gti_hp, color = Species)) +
  ylim(-2.5, 4) +
  xlim(-2.5, 4) +
  geom_point() +
  geom_abline() +
  labs(x = "Glow to Ignition (Epiradiator)", y = "Glow to Ignition (Hot Plate)", color = "Species") +
  scale_color_manual(values = c("#FC5130","#F7B801","#5F758E")) +
  annotate('text', x = -2.25, y = 3.75, label = 'e', size = 10) +
  theme_bw() + theme(axis.text = element_blank(),
                     aspect.ratio = 1/1,
                     axis.title = element_text(face = 'bold', size = 10),
                     legend.text = element_text(face = 'italic', size = 12),
                     legend.title = element_text(face = 'bold', size = 14))
gti.plot


ttfg.plot <- ggplot(df2, aes(x = ttfg_epi, y = ttfg_hp, color = Species)) +
  ylim(-2.5, 4) +
  xlim(-2.5, 4) +
  geom_point() +
  geom_abline() +
  labs(x = "Time to First Glow (Epiradiator)", y = "Time to First Glow (Hot Plate)", color = "Species") +
  scale_color_manual(values = c("#FC5130","#F7B801","#5F758E")) +
  annotate('text', x = -2.25, y = 3.75, label = 'h', size = 10) +
  theme_bw() + theme(axis.text = element_blank(),
                     aspect.ratio = 1/1,
                     axis.title = element_text(face = 'bold', size = 10),
                     legend.text = element_text(face = 'italic', size = 12),
                     legend.title = element_text(face = 'bold', size = 14))
ttfg.plot

temp.max.plot <- ggplot(df2, aes(x = temp_max_epi, y = temp_max_hp, color = Species)) +
   ylim(-2.5, 4) +
  xlim(-2.5, 4) +
  geom_point() +
  geom_abline() +
  labs(x = "Max Temp. (Epiradiator)", y = "Max Temp. (Hot Plate)", color = "Species") +
  scale_color_manual(values = c("#FC5130","#F7B801","#5F758E")) +
  annotate('text', x = -2.25, y = 3.75, label = 'd', size = 10) +
  theme_bw() + theme(axis.text = element_blank(),
                     aspect.ratio = 1/1,
                     axis.title = element_text(face = 'bold', size = 10),
                     legend.text = element_text(face = 'italic', size = 12),
                     legend.title = element_text(face = 'bold', size = 14))
temp.max.plot

pfg.plot <- ggplot(df2, aes(x = pfg_epi, y = pfg_hp, color = Species)) +
  ylim(-2.5, 4) +
  xlim(-2.5, 4) +
  geom_point() +
  geom_abline() +
  labs(x = "Post-Flame Glow (Epiradiator)", y = "Post-Flame Glow (Hot Plate)", color = "Species") +
  scale_color_manual(values = c("#FC5130","#F7B801","#5F758E")) +
  annotate('text', x = -2.25, y = 3.75, label = 'g', size = 10) +
  theme_bw() + theme(axis.text = element_blank(),
                     aspect.ratio = 1/1,
                     axis.title = element_text(face = 'bold', size = 10),
                     legend.text = element_text(face = 'italic', size = 12),
                     legend.title = element_text(face = 'bold', size = 14))
pfg.plot
```


Arranging above 8 plots
```{r}
ggarrange(tti.plot, fd.plot, fh.plot, temp.max.plot, gti.plot, gd.plot, pfg.plot, ttfg.plot, ncol = 4, nrow = 2, widths = c(1,1,1,1), heights = c(1,1), common.legend = TRUE, legend = 'right')

ggsave("figures/1to1graphsV2.jpg", height = 6, width = 12)
```


# ---------------------------------

# Now, Comparing Standard Deviations

## Summary Table 1 - by Model
```{r}
main_df %>% 
  select(fh, tti, ttfg, fd, gd, gti, temp_max, model) %>% 
  na.omit() %>% 
  tbl_summary(by = model, 
              statistic = list(all_continuous() ~ "{sd}"),
              label = list(fh ~ "Flame Height", 
              tti ~ "Time to Ignition", 
              ttfg ~ "Time to First Glow", 
              fd ~ "Flame Duration",
              gd ~ "Glow Duration", 
              gti ~ "Glow to Ignition",
              temp_max ~ "Maximum Temperature")) %>% 
  add_difference() %>% 
  modify_header(label ~ "**Flam. Metric**") %>% 
  modify_spanning_header(c("stat_1", "stat_2") ~ "**Model**")
```

## Summary Table 2 - by species, by model
```{r}
main_df %>% 
  select(fh, tti, ttfg, fd, gd, gti, temp_max, spp, model) %>% 
  tbl_strata(strata = spp, 
             .tbl_fun =
               ~ .x %>% 
               tbl_summary(by = model, missing = "no",
              statistic = list(all_continuous() ~ "{sd}"))) %>% 
  modify_header(label ~ "**Flam. Metric**")
```

## F-tests
```{r}
var.test(fh ~ model, data = main_df) #Significantly different variances

var.test(tti ~ model, data = main_df) #Significantly different variances

var.test(ttfg ~ model, data = main_df) #Significantly different variances

var.test(fd ~ model, data = main_df) #Significantly different variances

var.test(gd ~ model, data = main_df) #Significantly different variances

var.test(gti ~ model, data = main_df) #Significantly different variances

var.test(temp_max ~ model, data = main_df) #Not significantly different variances
```

# ---------------------------------

