---
title: "Binomial Regressions"
author: "Joe Celebrezze"
date: "3/16/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction
This .Rmd is for the binomial regressions of ignitions vs. non-ignitions in the method comparison dataset
See scripts/LOCAL/5.0_figures_2020.Rmd for the binomial regressions for the local species

# Loading in necessary packages
```{r, include = FALSE}
library(tidyverse)
library(cowplot)
library(here)
here = here::here
select = dplyr::select
library(janitor) # For data wrangling purposes including clean_names()
#Add in packages as necessary so no redundant packages
```

# Loading in datasets
Side note:
Oh boy. The dataset that we have been using has only the ignitions (no non-ignitions), so we are going to need to do some data wrangling prior to doing the binomial regressions. Rather than mess with the 4000+ line code where the data wrangling was initially done, I am just going to do the data wrangling myself -- good practice, right? 
*eyes narrow* 
right?
Let's see how this goes!
```{r, include = FALSE}
seki.raw.data <- read_csv(here("raw-data/SEKI_flammability.csv"))
local.raw.data <- read_csv(here("processed-data/compiled-datasets/LOCAL/local_flam_data_all.csv"))
```

# Data Wrangling (Yee-haw!)

## Local Dataset
```{r}
local.data <- local.raw.data %>% 
  clean_names() %>% 
  mutate(lfm = lfm_n_as_imputed) %>% 
  select(5:7, 13:38, lfm) %>%  #drop columns we dont want
  mutate(location = "local") %>% 
  unite(individual_round, c("individual", "round"), remove = FALSE)
```

Changing mpa to negative
```{r}
local.data <- local.data %>% 
  filter(mpa > 0) %>% 
  mutate(mpa = mpa*-1)
```

## SEKI Dataset
```{r}
seki.data <- seki.raw.data %>% 
  clean_names() %>% 
  unite(individual, c("year", "month", "spp", "sample"), remove = FALSE) %>% 
  unite(individual_round, c("individual", "round"), remove = FALSE) %>% 
  unite(year_month, c("year", "month"), remove = FALSE) %>% 
  select(-ttms, -bottle_wt) %>% 
  mutate(location = "seki")
```

## Combining the two
```{r}
all_methods_long <- rbind(seki.data, local.data)

all_methods_epi <- all_methods_long %>% 
  filter(model == "EPI")

all_methods_hp <- all_methods_long %>% 
  filter(model == "HP")

#Make a dataset that only has the rounds where we have paired EPI and HP samples
paired_methods_wide <- merge(all_methods_epi, all_methods_hp, by.x = "individual_round", by.y = "individual_round", suffixes = c("_epi", "_hp"))

paired_methods_epi <- paired_methods_wide %>% 
  select(1:31) %>% 
  rename_with(~str_remove(., '_epi'))

paired_methods_hp <- paired_methods_wide %>% 
  select(1, 32:61) %>% 
  rename_with(~str_remove(., '_hp'))

paired_methods_long <- bind_rows(paired_methods_epi, paired_methods_hp)
paired_methods_long <- paired_methods_long %>% 
  mutate(dw_flam_sample = (sample_wt * 100)/lfm)
```

## Writing new csv. files (in case we need these datasets again...)
```{r}
write_csv(paired_methods_long, here("processed-data", "compiled-datasets", "METHODS", "bothmethods_and_locations_long_noignitionsincluded.csv"))

write_csv(paired_methods_wide, here("processed-data", "compiled-datasets", "METHODS", "bothmethods_and_locations_wide_noignitionsincluded.csv"))
```

## Filtering out manual ignitions, species not-of-interest
```{r}
main.df <- paired_methods_long %>% 
  filter(spp != "QUKE",  spp != "PIJE", spp != "ABCO") %>% 
  filter(ignition != 2)
```

Changing up species, model names:
```{r}
main.df <- main.df %>% 
  mutate(Species = case_when(
    spp == "ADFA" ~ "A. fasciculatum", 
    spp == "CEME" ~ "C. megacarpus",
    spp == "CECO" ~ "C. cordulatus",
    spp == "ARPA" ~ "A. patula")) %>% 
  mutate(Model = case_when(
    model == "HP" ~ "Hot Plate",
    model == "EPI" ~ "Epiradiator"
  ))
```

# Binomial Regression - Stats Stuff
Since, for the rest of the methods comparison analyses, we have focused on ADFA, ARPA, CECO and CEME, these are the species we will focus on with the binomial regression

ADFA and CEME ignite all the time -- don't expect binomial regressions to work

## ADFA
```{r}
adfa.df <- main.df %>% 
  filter(spp == "ADFA")

m1 <- glm(ignition ~ lfm + site + sample_wt + model, data = adfa.df, family = "binomial")
summary(m1)
#not sig

m2 <- glm(ignition ~ mpa + site + sample_wt + model, data = adfa.df, family = "binomial")
summary(m2)
#not sig

m3 <- glm(ignition ~ dw_flam_sample + site + sample_wt + model, data = adfa.df, family = "binomial")
summary(m3)
#not sig
```

## ARPA
```{r}
arpa.df <- main.df %>% 
  filter(spp == "ARPA")

m1 <- glm(ignition ~ lfm + site + sample_wt + model, data = arpa.df, family = "binomial")
summary(m1)
#not sig

m2 <- glm(ignition ~ mpa + site + sample_wt + model, data = arpa.df, family = "binomial")
summary(m2)
#not sig

m3 <- glm(ignition ~ dw_flam_sample + site + sample_wt + model, data = arpa.df, family = "binomial")
summary(m3)
#not sig
```

## CECO
```{r}
ceco.df <- main.df %>% 
  filter(spp == "CECO") %>% 
  filter(lfm > 0)

m1 <- glm(ignition ~ lfm + site + sample_wt + model, data = ceco.df, family = "binomial")
summary(m1)
#not sig

m2 <- glm(ignition ~ mpa + site + sample_wt + model, data = ceco.df, family = "binomial")
summary(m2)
#not sig

m3 <- glm(ignition ~ dw_flam_sample + site + sample_wt + model, data = ceco.df, family = "binomial")
summary(m3)
#not sig
```

## CEME
```{r}
ceme.df <- main.df %>% 
  filter(spp == "CEME")

m1 <- glm(ignition ~ lfm + site + sample_wt + model, data = ceme.df, family = "binomial")
summary(m1)
#not sig

m2 <- glm(ignition ~ mpa + site + sample_wt + model, data = ceme.df, family = "binomial")
summary(m2)
#not sig

m3 <- glm(ignition ~ dw_flam_sample + site + sample_wt + model, data = ceme.df, family = "binomial")
summary(m3)
#not sig
```

# Data Visualization
## All species
```{r}
main.df %>% 
  ggplot(aes(x=mpa, y=ignition)) + 
  geom_point(alpha=.5) +
  facet_grid(model~spp) +
  stat_smooth(method="glm", se=FALSE, method.args = list(family=binomial)) +
  theme_bw() +
  labs(x = "Water Potential", y = "Ignition?", title = "Binomial Regression")

ggsave("figures/binomialregression.jpg", height = 7, width = 10)
```

## ARPA and CECO only
```{r}
mpa.bin.reg <- main.df %>% 
  filter(spp == "ARPA" | spp == "CECO") %>% 
  ggplot(aes(x=mpa, y=ignition)) + 
  scale_y_continuous(breaks = c(0,1)) +
  geom_point(alpha=.5) +
  facet_grid(Model~Species) +
  stat_smooth(method="glm", se=FALSE, method.args = list(family=binomial), color = 'black') +
  theme_bw() +
  theme(axis.title = element_text(face = 'bold', size = 14),
        strip.text.y = element_blank(),
        axis.text.y = element_text(size = 12),
        strip.text.x = element_text(face = 'bold.italic', size = 14)) +
  labs(x = "Water Potential", y = "Ignition?")

lfm.bin.reg <- main.df %>% 
  filter(spp == "ARPA" | spp == "CECO") %>%
  filter(lfm > 20) %>% 
  ggplot(aes(x=lfm, y=ignition)) + 
  scale_y_continuous(breaks = c(0,1)) +
  geom_point(alpha=.5) +
  facet_grid(Model~Species) +
  stat_smooth(method="glm", se=FALSE, method.args = list(family=binomial), color = 'black') +
  theme_bw() +
  theme(axis.title.x = element_text(face = 'bold', size = 14),
        axis.title.y = element_blank(),
        axis.text.y = element_blank(),
        strip.text.x = element_text(face = 'bold.italic', size = 14),
        strip.text.y = element_text(face = 'bold', size = 14)) +
  labs(x = "Live Fuel Moisture (%)", y = "Ignition?")

cowplot::plot_grid(ncol = 2, mpa.bin.reg, lfm.bin.reg)

ggsave("figures/binomialregression.2spp.jpg", height = 7, width = 14)
```
