---
title: "Classification and Regression Trees"
author: "Joe Celebrezze"
date: "4/5/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Loading in necessary packages
```{r, include = FALSE}
library(tidyverse)
select = dplyr::select
library(here)
here = here::here
library(rpart) # for classification and regression tree analysis
library(rpart.plot) # for cart visualization -- nicer than just plot()
#Add in packages as necessary so no redundant packages
```

# Loading in dataset
```{r, include = FALSE}
main_df <- read_csv(here("processed-data/compiled-datasets/METHODS/bothmethods_bothlocations_long.csv"))
```

# Data wrangling
```{r}
#Selecting columns of interest
df1 <- main_df %>% 
  select(spp, model, mpa, fh, ttfg, gti, tti, fd, gd, pfg, dw_flam_sample,
         lfm_outliers_out, start_temp, location, temp_max, ignition_temp, sample_wt)
```

# Try 1
Going to try a relatively simple one with only species, model and water status
```{r}
tti.cfit <- rpart(tti ~ spp + model + mpa, data = df1, method = "class", cp = 0.011765)
print(tti.cfit)
printcp(tti.cfit)
prp(tti.cfit, type = 5, branch = 1)
```

cp = cost-penalty parameter; limits the complexity of the tree
  pruning parameter, tells R how high up to prune the tree
  try out 0.001
  
First lowest xerror and add standard deviation then choose the first xerror level below that
  
Including all variables might not affect the top of the tree which is what matters for us

Try to predict ignition = 1 or 0

Normalize by sample weight? Scale and center?

# Post-meeting-with-Max

# Data Wrangling

## Normalizing flam. metrics
```{r}
df_norm <- df1 %>% 
  mutate(tti_norm = tti/sample_wt) %>% 
  mutate(fd_norm = fd/sample_wt)
# Splitting into hp and epi dataframes
hpdf_norm <- df_norm %>% 
  filter(model == "HP")
epidf_norm <- df_norm %>% 
  filter(model == "EPI")
```

## Scaling/centering flam. metrics
```{r}
# Splitting dataset by epi vs. hot plate prior to scaling/centering
epi_df <- df1 %>% 
  filter(model == "EPI") %>% 
  na.omit()
hp_df <- df1 %>% 
  filter(model == "HP") %>% 
  na.omit()


epidf_sc <- epi_df %>% 
  mutate(fh = fh - mean(fh), fd = fd - mean(fd), ttfg = ttfg - mean(ttfg), gti = gti -
          mean(gti), tti = tti - mean(tti), gd = gd - mean(gd), pfg = pfg - mean(pfg),
          temp_max = temp_max - mean(temp_max)) %>%  #centering
  mutate(fh = scale(fh), fd = scale(fd), ttfg = scale(ttfg), gti = scale(gti), tti =
           scale(tti), gd = scale(gd), pfg = scale(pfg), temp_max = scale(temp_max)) #scaled

hpdf_sc <- hp_df %>% 
  mutate(fh = fh - mean(fh), fd = fd - mean(fd), ttfg = ttfg - mean(ttfg), gti = gti -
          mean(gti), tti = tti - mean(tti), gd = gd - mean(gd), pfg = pfg - mean(pfg),
          temp_max = temp_max - mean(temp_max)) %>%  #centering
  mutate(fh = scale(fh), fd = scale(fd), ttfg = scale(ttfg), gti = scale(gti), tti =
           scale(tti), gd = scale(gd), pfg = scale(pfg), temp_max = scale(temp_max)) #scaled

df_sc <- rbind(hpdf_sc, epidf_sc) # combining two methods together in one dataset
```

## Normalizing and then Scaling/Centering
For now, just focusing on time to ignition and flame duration, so I hashed out all of the other flam. metrics (but will likely need to return to them and streamline the code a bit)
```{r}
epidf_nsc <- epidf_norm %>% 
  na.omit() %>% 
  mutate(tti_norm = tti_norm - mean(tti_norm), fd_norm = fd_norm - mean(fd_norm)) %>% #centered
  mutate(tti_norm = scale(tti_norm), fd_norm = scale(fd_norm)) #scaled

  #mutate(fh_norm = fh_norm - mean(fh_norm), fd_norm = fd_norm - mean(fd_norm), ttfg_norm = ttfg_norm - mean(ttfg_norm), gti = gti -
          #mean(gti), tti = tti - mean(tti), gd = gd - mean(gd), pfg = pfg - mean(pfg),
          #temp_max = temp_max - mean(temp_max)) %>%  #centering
  #mutate(fh_norm = scale(fh_norm), fd_norm = scale(fd_norm), ttfg_norm = scale(ttfg_norm), gti = scale(gti), tti =
           #scale(tti), gd = scale(gd), pfg = scale(pfg), temp_max = scale(temp_max)) #scaled

hpdf_nsc <- hpdf_norm %>% 
  na.omit() %>% 
  mutate(tti_norm = tti_norm - mean(tti_norm), fd_norm = fd_norm - mean(fd_norm)) %>% #centered
  mutate(tti_norm = scale(tti_norm), fd_norm = scale(fd_norm)) #scaled

  #mutate(fh_norm = fh_norm - mean(fh_norm), fd_norm = fd_norm - mean(fd_norm), ttfg_norm = ttfg_norm - mean(ttfg_norm), gti = gti -
          #mean(gti), tti = tti - mean(tti), gd = gd - mean(gd), pfg = pfg - mean(pfg),
          #temp_max = temp_max - mean(temp_max)) %>%  #centering
  #mutate(fh_norm = scale(fh_norm), fd_norm = scale(fd_norm), ttfg_norm = scale(ttfg_norm), gti = scale(gti), tti =
           #scale(tti), gd = scale(gd), pfg = scale(pfg), temp_max = scale(temp_max)) #scaled

df_nsc <- rbind(hpdf_nsc, epidf_nsc)
```


# TTI

## Normalized by sample weight
```{r}
tti.norm.cfit <- rpart(tti_norm ~ spp + mpa, data = df_norm, method = "class")
printcp(tti.norm.cfit)
prp(tti.norm.cfit, type = 5, branch = 1)
# Type = determines the appearance of the tree -- I liked type = 5 the most. Branch = 1 means square-shouldered branches; branch = 0 are angular branches and anything in between 0 and 1 are varying levels of squareness
```
Okay, so when normalized by sample weight, model is not a major split in the data! This is interesting.

Also, mess with prp plotting later -- there are SO many arguments in this one function!

Splitting into hot plate and epiradiator to see how trees compare
```{r}
tti.n.hp.cfit <- rpart(tti_norm ~ spp + mpa, data = hpdf_norm, method = "class")
printcp(tti.n.hp.cfit)
prp(tti.n.hp.cfit, type = 5, branch = 1)

tti.n.epi.cfit <- rpart(tti_norm ~ spp + mpa, data = epidf_norm, method = "class")
printcp(tti.n.epi.cfit)
prp(tti.n.epi.cfit, type = 5, branch = 1)
```

## Scaled and Centered

### Two models together
```{r}
tti.sc.cfit <- rpart(tti ~ spp + mpa + model + sample_wt, data = df_sc, method = "class")
# Including sample.wt in the above to try and see if that could be what is driving initial split rather than model
printcp(tti.sc.cfit)
prp(tti.sc.cfit, type = 5, branch = 1)
```

### Two models split up
```{r}
tti.sc.hp.cfit <- rpart(tti ~ spp + mpa + sample_wt, data = hpdf_sc, method = "class")
printcp(tti.sc.hp.cfit)
prp(tti.sc.hp.cfit, type = 5, branch = 1)
# Interestingly enough, sample weight appears to be a MAJOR driver in time to ignition for the hot plate chamber

tti.sc.epi.cfit <- rpart(tti ~ spp + mpa + sample_wt, data = epidf_sc, method = "class")
printcp(tti.sc.epi.cfit)
prp(tti.sc.epi.cfit, type = 5, branch = 1)
```

## Normalized and then Scaled and Centered

### Two models together
```{r}
tti.nsc.cfit <- rpart(tti_norm ~ spp + mpa, data = df_nsc, method = "class")
printcp(tti.nsc.cfit)
prp(tti.nsc.cfit, type = 5, branch = 1)
```

### Models split up
```{r}
tti.nsc.hp.cfit <- rpart(tti_norm ~ spp + mpa, data = hpdf_nsc, method = "class")
printcp(tti.nsc.hp.cfit)
prp(tti.nsc.hp.cfit, type = 5, branch = 1)

tti.nsc.epi.cfit <- rpart(tti_norm ~ spp + mpa, data = epidf_nsc, method = "class")
printcp(tti.nsc.epi.cfit)
prp(tti.nsc.epi.cfit, type = 5, branch = 1)
```

# FLAME DURATION

## No data manipulation
```{r}
fd.cfit <- rpart(fd ~ spp + model + mpa, data = df1, method = "class", cp = 0.013)
printcp(fd.cfit)
prp(fd.cfit, type = 5, branch = 1)

fd.cfit2 <- rpart(fd ~ spp + model + mpa + sample_wt, data = df1, method = "class", cp = 0.017)
printcp(fd.cfit2)
prp(fd.cfit2, type = 5, branch = 1)
```

## Normalized
### Both Methods
```{r}
fd.norm.cfit <- rpart(fd_norm ~ spp + mpa + model, data = df_norm, method = "class")
printcp(fd.norm.cfit)
prp(fd.norm.cfit, type = 5, branch = 1)
```

### Methods side-by-side
```{r}
fd.n.hp.cfit <- rpart(fd_norm ~ spp + mpa, data = hpdf_norm, method = "class")
printcp(fd.n.hp.cfit)
prp(fd.n.hp.cfit, type = 5, branch = 1)

fd.n.epi.cfit <- rpart(fd_norm ~ spp + mpa, data = epidf_norm, method = "class")
printcp(fd.n.epi.cfit)
prp(fd.n.epi.cfit, type = 5, branch = 1)
```

## Scaled and Centered
### Both Methods
```{r}
tti.sc.cfit <- rpart(tti ~ spp + mpa + model + sample_wt, data = df_sc, method = "class")
# Including sample.wt in the above to try and see if that could be what is driving initial split rather than model
printcp(tti.sc.cfit)
prp(tti.sc.cfit, type = 5, branch = 1)
```

### Methods side-by-side
```{r}
tti.sc.hp.cfit <- rpart(tti ~ spp + mpa + sample_wt, data = hpdf_sc, method = "class")
printcp(tti.sc.hp.cfit)
prp(tti.sc.hp.cfit, type = 5, branch = 1)
# Interestingly enough, sample weight appears to be a MAJOR driver in time to ignition for the hot plate chamber

tti.sc.epi.cfit <- rpart(tti ~ spp + mpa + sample_wt, data = epidf_sc, method = "class")
printcp(tti.sc.epi.cfit)
prp(tti.sc.epi.cfit, type = 5, branch = 1)
```

