---
title: "Converting HP Data into EPI format"
author: "Joe Celebrezze"
date: '2022-09-13'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Loading in necessary packages
```{r, include = FALSE}
library(tidyverse)
select = dplyr::select
library(here)
here = here::here
library(ggpubr) # To arrange multiple plots with ggarrange
library(gtsummary) # For summary tables
library(gt) # For summary tables
library(remef) # To remove partial effects for visualization
library(lme4)
library(sjPlot)
library(psych)
library(gridExtra)
library(grid)
#Add in packages as necessary so no redundant packages
```

# Loading in datasets
```{r, include = FALSE}
main_df <- read_csv(here("processed-data/compiled-datasets/METHODS/bothmethods_bothlocations_long.csv"))
wide_df <- read_csv(here("processed-data/compiled-datasets/METHODS/bothmethods_bothlocations_wide.csv"))
```

# Taking out NA values
For the two individuals we are taking out -- These have NAs as tti values and keeping these in screws up the data analysis, and we have no way of imputing the data with any sort of confidence
For the ignition = 0 values, we are only interested in instances when the sample ignited for the following analyses
```{r}
main_df <- main_df %>% 
  filter(individual_round != "2020_September_ADFA_1.2_1") %>% 
  filter(individual_round != "2020_September_ADFA_2.6_9") %>% 
  filter(ignition == 1)

wide_df <- wide_df %>% 
  filter(individual_round != "2020_September_ADFA_1.2_1") %>% 
  filter(individual_round != "2020_September_ADFA_2.6_9") %>% 
  filter(ignition_epi == 1)
```

# Scaling and Centering

Below, I scaled and centered the flam. metrics according to each model. Without separating by model, it scales/centers by the results (i.e. by standard deviations, means) of both models together in one pool which does not make sense when comparing the two models separately.

```{r}
epi_df <- main_df %>% 
  filter(model == "EPI")
hp_df <- main_df %>% 
  filter(model == "HP")


epi_df1 <- epi_df %>% 
  mutate(fh = fh - mean(fh), fd = fd - mean(fd), ttfg = ttfg - mean(ttfg), gti = gti -
          mean(gti), tti = tti - mean(tti), gd = gd - mean(gd), pfg = pfg - mean(pfg),
          temp_max = temp_max - mean(temp_max), sample_wt = sample_wt - mean(sample_wt),
         dw_flam_sample = dw_flam_sample - mean(dw_flam_sample)) %>%  #centering
  mutate(fh = scale(fh), fd = scale(fd), ttfg = scale(ttfg), gti = scale(gti), tti =
           scale(tti), gd = scale(gd), pfg = scale(pfg), temp_max = scale(temp_max),
           sample_wt = scale(sample_wt), dw_flam_sample = scale(dw_flam_sample)) #scaled

hp_df1 <- hp_df %>% 
  mutate(fh = fh - mean(fh), fd = fd - mean(fd), ttfg = ttfg - mean(ttfg), gti = gti -
          mean(gti), tti = tti - mean(tti), gd = gd - mean(gd), pfg = pfg - mean(pfg),
          temp_max = temp_max - mean(temp_max), sample_wt = sample_wt - mean(sample_wt),
         dw_flam_sample = dw_flam_sample - mean(dw_flam_sample)) %>%  #centering
  mutate(fh = scale(fh), fd = scale(fd), ttfg = scale(ttfg), gti = scale(gti), tti =
           scale(tti), gd = scale(gd), pfg = scale(pfg), temp_max = scale(temp_max),
           sample_wt = scale(sample_wt), dw_flam_sample = scale(dw_flam_sample)) #scaled
```

Stitching epi_df1 and hp_df1 together:
```{r}
both_df1 <- bind_rows(epi_df1, hp_df1)
```

# Looking at differences in means
```{r}
epi_df %>% 
  select(tti, fd, fh, gd, gti, pfg, ttfg, temp_max, sample_wt) %>% 
  summary()

hp_df %>% 
  select(tti, fd, fh, gd, gti, pfg, ttfg, temp_max, sample_wt) %>% 
  summary()

epi.means <- c(39.12, 6.681, 8.811, 121.53, 24.01, 89.05, 14.61, 316.6, 0.5108)
hp.means <- c(94.86, 17.26, 22.85, 151.3, 23.62, 108.3, 70.28, 300.1, 2.1363)
div.means <- hp.means/epi.means
div.means
```

# Looking at normalized values
Normalizing using sample weight
```{r}
normalized_df <- main_df %>% 
  select(tti, fd, fh, gd, sample_wt, mpa, lfm_outliers_out, spp, model, year_month) %>% 
  mutate(tti = tti/sample_wt, fd = fd/sample_wt, fh = fh/sample_wt, gd = gd/sample_wt)
```

```{r}
normalized_df %>% 
  select(tti, fd, fh, gd, model) %>% 
  filter(model == "EPI") %>% 
  summary()
epi.means <- c(76.95, 13.103, 17.307, 238.71)

normalized_df %>% 
  select(tti, fd, fh, gd, model) %>% 
  filter(model == "HP") %>% 
  summary()
hp.means <- c(54.564, 9.344, 12.494, 80.461)

div.means <- epi.means/hp.means
```

From the above, we see -- after normalization by sample weight -- TTI, FD and FH have similar conversion factors to make the means of the EPI (normalized) and the HP (normalized) similar (conv factor = ~1.4), but glow duration acts differently which matches the PCA results as well. The conversion factor for GD = ~3.0. Going to use these conversion factors on the HP values and then attempt to calculate a flammability proxy by using a PCA on this renewed dataset.

# Conversion factors
```{r}
epi_norm_df <- normalized_df %>% 
  filter(model == "EPI")

hp_conv_df <- normalized_df %>% 
  filter(model == "HP") %>% 
  mutate(tti = 1.4*tti, fd = 1.4*fd, fh = 1.4*fh, gd = 3.0*gd)

conv_df <- rbind(epi_norm_df, hp_conv_df)
```

# PCA
Here I am going to do a PCA on the new dataset to see how heavily each of the four metrics are loaded on the principal components to get a better sense of how we want to calculate a flam. proxy
```{r}
#decisions for plotting:
choices = 1:2 
scale = 1
obs.scale = 1 - scale
var.scale = scale
ellipse.prob = 0.68
labels.size = 3
circle.prob = 0.69
choices = 1:2

#Run PCA
pcobj <- conv_df %>% 
  select(tti, fd, fh, gd) %>% 
  prcomp(center = TRUE, scale = TRUE) #Running PCA

# extract PCA components: 
nobs.factor <- sqrt(nrow(pcobj$x) - 1)
    d <- pcobj$sdev
    u <- sweep(pcobj$x, 2, 1/(d * nobs.factor), FUN = "*")
    v <- pcobj$rotation

  choices <- pmin(choices, ncol(u))
  df.u <- as.data.frame(sweep(u[, choices], 2, d[choices]^obs.scale, 
                              FUN = "*"))
  v <- sweep(v, 2, d^var.scale, FUN = "*")
  df.v <- as.data.frame(v[, choices])
  names(df.u) <- c("PC1", "PC2")
  names(df.v) <- names(df.u)
  df.u <- df.u * nobs.factor

  r <- sqrt(qchisq(circle.prob, df = 2)) * prod(colMeans(df.u^2))^(1/4)
  
v.scale <- rowSums(v^2)
df.v <- r * df.v/sqrt(max(v.scale)) 
df.v <- df.v %>% mutate(PC1, PC2)
df.v$Variables <- rownames(v) 
PCAloadings = df.v
#df.v = dataset with loadings 
```

The following are the loadings for PC1:
tti: 1.1216275
fh: 0.8717786
fd: 0.8168248
gd: 1.2105129

To simplify the formula a bit, I am going to try 1.15 for TTI and GD and then 0.85 for FH and FD

# Trying out some flammability proxies
1) Adding together tti, fh, fd, gd after multiplying by above loading estimates
```{r}
conv_df <- conv_df %>% 
  mutate(flam.proxy.add = 1.15*tti+0.85*fh+0.85*fd+1.15*gd)

ggplot(conv_df, aes(x = flam.proxy.add, y = mpa, color = model)) +
  geom_point() +
  geom_smooth(method = 'lm', se = F)
```
This makes GD way too involved in the calculation of the flam. proxy

2) Scaling prior to adding together
```{r}
conv_df <- conv_df %>% 
  dplyr::group_by(model) %>% 
  mutate(tti.scaled = scale(tti), fh.scaled = scale(fh), fd.scaled = scale(fd), gd.scaled = scale(gd)) %>% 
  mutate(flam.proxy.scale.add = 1.15*tti.scaled+0.85*fh.scaled+0.85*fd.scaled+1.15*gd.scaled) %>% 
  ungroup()

ggplot(conv_df, aes(x = flam.proxy.scale.add, y = gd, color = model)) +
  geom_point() +
  geom_smooth(method = 'lm', se = F)
```
This looks better, but it does not make conceptual sense to add all of these variables together. TTI, at least, should be subtracted, as a higher value represents *less* ignitable

3) Scaled values, subtracting tti
```{r}
conv_df <- conv_df %>% 
  mutate(flam.proxy.scale.subtract = -1.15*tti.scaled + 0.85*fh.scaled + 0.85*fd.scaled + 1.15*gd.scaled)

ggplot(conv_df, aes(y = flam.proxy.scale.subtract, x = mpa, color = model)) +
  geom_point() +
  geom_smooth(method = 'lm', se = F)
```
This looks like the best option yet, but let's try some other ways of calculating the proxy

4) Multiplying values
In order to multiply values in a way that makes sense, we need to shift the scaled data so that the minimum value = 1 and we need to flip the TTI data so that high values represent highly ignitable samples
```{r}
conv_df %>% 
  select(tti.scaled, fh.scaled, fd.scaled, gd.scaled) %>% 
  summary()

conv_df <- conv_df %>% 
  mutate(tti.scaled.pos = (tti.scaled -4.323980)*-1, fh.scaled.pos = fh.scaled + 3.0338229, fd.scaled.pos = fd.scaled + 2.290741, gd.scaled.pos = gd.scaled + 3.536216) %>% 
  mutate(flam.proxy.multiply = tti.scaled.pos*fh.scaled.pos*fd.scaled.pos*gd.scaled.pos)

ggplot(conv_df, aes(y = flam.proxy.multiply, x = mpa, color = model)) +
  geom_point() +
  geom_smooth(method = 'lm', se = F)
```
This worsened the proxy relative to (3)

