---
title: "Manual Ignitions for Hot Plate Burns (CECO)"
author: "Joe Celebrezze"
date: "8/4/2022"
output: html_document
---

# Set-up
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(here)
library(lme4) # mixed effects models
library(performance)
library(cowplot)
library(gridExtra)
library(grid)
library(gghighlight)
library(ggpubr)
here = here::here
select = dplyr::select
col3 = hcl.colors(10, "YlOrRd", rev = TRUE) #color scale to use for consistency 
```

Reading in dataframe
```{r}
paired_methods_long <- read.csv(here("processed-data", "compiled-datasets", "METHODS", "bothm_bothl_manual_ignitions_in.csv"))

epi.df <- paired_methods_long %>% 
  filter(model == "EPI" & ignition == 1) # n = 96

hp.df <- paired_methods_long %>% 
  filter(model == "HP") %>% 
  filter(ignition == 1 | ignition == 2) # n = 112
```

# --------------------------------

# CECO Across Models

- Hot plate burns are manual ignitions
- Epiradiator burns are natural ignitions
- I must scale and center for each prior to analysis

## Scaling Method 1
Scaling and centering for only CECO, for each model
```{r}
epi.df.ceco <- epi.df %>% 
  filter(spp == "CECO") %>% 
  mutate(fh = fh - mean(fh), fd = fd - mean(fd), ttfg = ttfg - mean(ttfg), gti = gti -
          mean(gti), tti = tti - mean(tti), gd = gd - mean(gd), pfg = pfg - mean(pfg),
          temp_max = temp_max - mean(temp_max), dw_scaled = dw_flam_sample - mean(dw_flam_sample)) %>%  #centered
  mutate(fh = scale(fh), fd = scale(fd), ttfg = scale(ttfg), gti = scale(gti), tti =
           scale(tti), gd = scale(gd), pfg = scale(pfg), temp_max = scale(temp_max), dw_scaled = scale(dw_scaled)) #scaled
hp.df.ceco <- hp.df %>% 
  filter(spp == "CECO") %>% 
  mutate(fh = fh - mean(fh), fd = fd - mean(fd), ttfg = ttfg - mean(ttfg), gti = gti -
          mean(gti), tti = tti - mean(tti), gd = gd - mean(gd), pfg = pfg - mean(pfg),
          temp_max = temp_max - mean(temp_max), dw_scaled = dw_flam_sample - mean(dw_flam_sample)) %>%  #centering
  mutate(fh = scale(fh), fd = scale(fd), ttfg = scale(ttfg), gti = scale(gti), tti =
           scale(tti), gd = scale(gd), pfg = scale(pfg), temp_max = scale(temp_max), dw_scaled = scale(dw_scaled)) #scaled
df.ceco <- rbind(epi.df.ceco, hp.df.ceco)
```

## TTI
We would expect the time to ignition to have differrent relationships for manual vs. non-manual ignitions. 
### vs. Dry Weight
Model:
```{r}
tti.dw.noint <- lmer(tti ~ dw_scaled + model + site + (1|individual), data = df.ceco)
tti.dw.int <- lmer(tti ~ dw_scaled*model + site + (1|individual), data = df.ceco)
# No interaction performs better
summary(tti.dw.noint)
```

```{r}
tti.dw.plot <- df.ceco %>%
  ggplot(aes(x = dw_scaled, y = tti, color = model)) +
  labs(x = "Dry Weight (g)", y = "Time to Ignition (s)", color = "Model") +
  geom_point(size = 1, alpha = 0.6) +
  geom_abline(slope = -0.1839, intercept = 0.01746, color = "#F5A400", cex = 0.8, alpha = 0.4) +
  geom_abline(slope = -0.1839, intercept = 0.0174600000000008657, color = "#7D0025", cex = 0.8, alpha = 0.4) +
  theme_bw() +
  scale_color_manual(values = c("#F5A400", "#7D0025")) +
  theme(axis.title = element_text(face = 'bold'),
        legend.title = element_text(face = 'bold'),
        #axis.title.x = element_blank(),
        legend.position = 'right')
tti.dw.plot
```

### vs. LFM
Model:
```{r}
tti.lfm.noint <- lmer(tti ~ lfm + model + site + (1|individual), data = df.ceco)
tti.lfm.int <- lmer(tti ~ lfm*model + site + (1|individual), data = df.ceco)
performance(tti.lfm.int)
# No interaction performs better
summary(tti.lfm.noint)
```

```{r}
tti.lfm.plot <- df.ceco %>%
  ggplot(aes(x = lfm, y = tti, color = model)) +
  labs(x = "Live Fuel Moisture", y = "Time to Ignition (s)", color = "Model") +
  geom_point(size = 1, alpha = 0.6) +
  geom_abline(slope = 0.01427, intercept = -1.115, color = "#F5A400", cex = 0.8, alpha = 0.4) +
  geom_abline(slope = 0.01427, intercept = -1.115000000000005011, color = "#7D0025", cex = 0.8, alpha = 0.4) +
  theme_bw() +
  scale_color_manual(values = c("#F5A400", "#7D0025")) +
  theme(axis.title = element_text(face = 'bold'),
        legend.title = element_text(face = 'bold'),
        #axis.title.x = element_blank(),
        legend.position = 'right')
tti.lfm.plot
```

### vs. MPa
Model:
```{r}
tti.mpa.noint <- lmer(tti ~ mpa + model + site + (1|individual), data = df.ceco)
tti.mpa.int <- lmer(tti ~ mpa*model + site + (1|individual), data = df.ceco)
performance(tti.mpa.noint)
# No interaction performs better
summary(tti.mpa.noint)
```

```{r}
tti.mpa.plot <- df.ceco %>%
  ggplot(aes(x = mpa, y = tti, color = model)) +
  labs(x = "Water Potential (MPa)", y = "Time to Ignition (s)", color = "Model") +
  geom_point(size = 1, alpha = 0.6) +
  geom_abline(slope = 0.1172, intercept = 0.5028, color = "#F5A400", cex = 0.8, alpha = 0.4) +
  geom_abline(slope = 0.1172, intercept = 0.5028, color = "#7D0025", cex = 0.8, alpha = 0.4) +
  theme_bw() +
  scale_color_manual(values = c("#F5A400", "#7D0025")) +
  theme(axis.title = element_text(face = 'bold'),
        legend.title = element_text(face = 'bold'),
        #axis.title.x = element_blank(),
        legend.position = 'right')
tti.mpa.plot
```

Hmmmm... I wonder if scaling and centering the metrics prior to splitting the dataset would change the conclusions. I think the species differences analysis may give us some insight into this. For now, I am going to try a different scaling method

## Scaling Method 2
- Scaling and centering prior to splitting by species
```{r}
epi.df1 <- epi.df %>%  
  mutate(fh = fh - mean(fh), fd = fd - mean(fd), ttfg = ttfg - mean(ttfg), gti = gti -
          mean(gti), tti = tti - mean(tti), gd = gd - mean(gd), pfg = pfg - mean(pfg),
          temp_max = temp_max - mean(temp_max), dw_scaled = dw_flam_sample - mean(dw_flam_sample)) %>%  #centered
  mutate(fh = scale(fh), fd = scale(fd), ttfg = scale(ttfg), gti = scale(gti), tti =
           scale(tti), gd = scale(gd), pfg = scale(pfg), temp_max = scale(temp_max), dw_scaled = scale(dw_scaled)) #scaled
hp.df1 <- hp.df %>% 
  mutate(fh = fh - mean(fh), fd = fd - mean(fd), ttfg = ttfg - mean(ttfg), gti = gti -
          mean(gti), tti = tti - mean(tti), gd = gd - mean(gd), pfg = pfg - mean(pfg),
          temp_max = temp_max - mean(temp_max), dw_scaled = dw_flam_sample - mean(dw_flam_sample)) %>%  #centering
  mutate(fh = scale(fh), fd = scale(fd), ttfg = scale(ttfg), gti = scale(gti), tti =
           scale(tti), gd = scale(gd), pfg = scale(pfg), temp_max = scale(temp_max), dw_scaled = scale(dw_scaled)) #scaled

hp.df.ceco1 <- hp.df1 %>% 
  filter(spp == "CECO")
epi.df.ceco1 <- epi.df1 %>% 
  filter(spp == "CECO")

df.ceco1 <- rbind(epi.df.ceco1, hp.df.ceco1)
```

## TTI
### vs. Dry Weight
Model:
```{r}
tti.dw.noint <- lmer(tti ~ dw_scaled + model + site + (1|individual), data = df.ceco1)
tti.dw.int <- lmer(tti ~ dw_scaled*model + site + (1|individual), data = df.ceco1)
performance(tti.dw.int)
# No interaction performs better
summary(tti.dw.noint)
```

```{r}
tti.dw.plot2 <- df.ceco1 %>%
  ggplot(aes(x = dw_scaled, y = tti, color = model)) +
  labs(x = "Dry Weight (g)", y = "Time to Ignition (s)", color = "Model") +
  geom_point(size = 1, alpha = 0.6) +
  geom_abline(slope = -0.15851, intercept = -0.36858, color = "#F5A400", cex = 0.8, alpha = 0.8) +
  geom_abline(slope = -0.15851, intercept = 1.42616, color = "#7D0025", cex = 0.8, alpha = 0.8) +
  theme_bw() +
  scale_color_manual(values = c("#F5A400", "#7D0025")) +
  theme(axis.title = element_text(face = 'bold'),
        legend.title = element_text(face = 'bold'),
        #axis.title.x = element_blank(),
        legend.position = 'right')
tti.dw.plot2
```

### vs. LFM
Model:
```{r}
tti.lfm.noint <- lmer(tti ~ lfm + model + site + (1|individual), data = df.ceco1)
tti.lfm.int <- lmer(tti ~ lfm*model + site + (1|individual), data = df.ceco1)
performance(tti.lfm.noint)
# No interaction performs better
summary(tti.lfm.noint)
```

```{r}
tti.lfm.plot2 <- df.ceco1 %>%
  ggplot(aes(x = lfm, y = tti, color = model)) +
  labs(x = "Live Fuel Moisture", y = "Time to Ignition (s)", color = "Model") +
  geom_point(size = 1, alpha = 0.6) +
  geom_abline(slope = 0.012425, intercept = -1.350994, color = "#F5A400", cex = 0.8, alpha = 0.8) +
  geom_abline(slope = 0.012425, intercept = 0.504808, color = "#7D0025", cex = 0.8, alpha = 0.8) +
  theme_bw() +
  scale_color_manual(values = c("#F5A400", "#7D0025")) +
  theme(axis.title = element_text(face = 'bold'),
        legend.title = element_text(face = 'bold'),
        #axis.title.x = element_blank(),
        legend.position = 'right')
tti.lfm.plot2
```

### vs. MPa
Model:
```{r}
tti.mpa.noint <- lmer(tti ~ mpa + model + site + (1|individual), data = df.ceco1)
tti.mpa.int <- lmer(tti ~ mpa*model + site + (1|individual), data = df.ceco1)
performance(tti.mpa.noint)
# No interaction performs better
summary(tti.mpa.noint)
```

```{r}
tti.mpa.plot2 <- df.ceco1 %>%
  ggplot(aes(x = mpa, y = tti, color = model)) +
  labs(x = "Water Potential (MPa)", y = "Time to Ignition (s)", color = "Model") +
  geom_point(size = 1, alpha = 0.6) +
  geom_abline(slope = 0.10175, intercept = 0.05654, color = "#F5A400", cex = 0.8, alpha = 0.8) +
  geom_abline(slope = 0.10175, intercept = 1.91234, color = "#7D0025", cex = 0.8, alpha = 0.8) +
  theme_bw() +
  scale_color_manual(values = c("#F5A400", "#7D0025")) +
  theme(axis.title = element_text(face = 'bold'),
        legend.title = element_text(face = 'bold'),
        #axis.title.x = element_blank(),
        legend.position = 'right')
tti.mpa.plot2
```

## FH
### vs. Dry Weight
Model:
```{r}
fh.dw.noint <- lmer(fh ~ dw_scaled + model + site + (1|individual), data = df.ceco1)
fh.dw.int <- lmer(fh ~ dw_scaled*model + site + (1|individual), data = df.ceco1)
performance(fh.dw.noint)
# No interaction performs better
summary(fh.dw.noint)
```

```{r}
fh.dw.plot2 <- df.ceco1 %>%
  ggplot(aes(x = dw_scaled, y = fh, color = model)) +
  labs(x = "Dry Weight (g)", y = "Flame Height (cm)", color = "Model") +
  geom_point(size = 1, alpha = 0.6) +
  geom_abline(slope = 0.4774, intercept = -0.2389, color = "#F5A400", cex = 0.8, alpha = 0.8) +
  geom_abline(slope = 0.4774, intercept = -0.4477, color = "#7D0025", cex = 0.8, alpha = 0.8) +
  theme_bw() +
  scale_color_manual(values = c("#F5A400", "#7D0025")) +
  theme(axis.title = element_text(face = 'bold'),
        legend.title = element_text(face = 'bold'),
        #axis.title.x = element_blank(),
        legend.position = 'right')
fh.dw.plot2
```

### vs. LFM
Model:
```{r}
fh.lfm.noint <- lmer(fh ~ lfm + model + site + (1|individual), data = df.ceco1)
fh.lfm.int <- lmer(fh ~ lfm*model + site + (1|individual), data = df.ceco1)
performance(fh.lfm.int)
# No interaction performs better
summary(fh.lfm.noint)
```

```{r}
fh.lfm.plot2 <- df.ceco1 %>%
  ggplot(aes(x = lfm, y = fh, color = model)) +
  labs(x = "Live Fuel Moisture", y = "Flame Height (cm)", color = "Model") +
  geom_point(size = 1, alpha = 0.6) +
  geom_abline(slope = -0.004855, intercept = 0.247181, color = "#F5A400", cex = 0.8, alpha = 0.8) +
  geom_abline(slope = -0.004855, intercept = -0.145535, color = "#7D0025", cex = 0.8, alpha = 0.8) +
  theme_bw() +
  scale_color_manual(values = c("#F5A400", "#7D0025")) +
  theme(axis.title = element_text(face = 'bold'),
        legend.title = element_text(face = 'bold'),
        #axis.title.x = element_blank(),
        legend.position = 'right')
fh.lfm.plot2
```

### vs. MPa
Model:
```{r}
fh.mpa.noint <- lmer(fh ~ mpa + model + site + (1|individual), data = df.ceco1)
fh.mpa.int <- lmer(fh ~ mpa*model + site + (1|individual), data = df.ceco1)
performance(fh.mpa.int)
# At odds with each other (not sig. difference, lower AIC for interactions, lower BIC for no interactions), will lean towards including interaction term I suppose
summary(fh.mpa.int)
```

```{r}
fh.mpa.plot2 <- df.ceco1 %>%
  ggplot(aes(x = mpa, y = fh, color = model)) +
  labs(x = "Water Potential (MPa)", y = "Flame Height (cm)", color = "Model") +
  geom_point(size = 1, alpha = 0.6) +
  geom_abline(slope = -0.21028, intercept = -1.01037, color = "#F5A400", cex = 0.8, alpha = 0.8) +
  geom_abline(slope = 0.0236, intercept = -0.48115, color = "#7D0025", cex = 0.8, alpha = 0.8) +
  theme_bw() +
  scale_color_manual(values = c("#F5A400", "#7D0025")) +
  theme(axis.title = element_text(face = 'bold'),
        legend.title = element_text(face = 'bold'),
        #axis.title.x = element_blank(),
        legend.position = 'right')
fh.mpa.plot2
```

## Max Temp.
### vs. Dry Weight
Model:
```{r}
temp_max.dw.noint <- lmer(temp_max ~ dw_scaled + model + site + (1|individual), data = df.ceco1)
temp_max.dw.int <- lmer(temp_max ~ dw_scaled*model + site + (1|individual), data = df.ceco1)
performance(temp_max.dw.int)
# No interaction performs better
summary(temp_max.dw.noint)
```

```{r}
temp_max.dw.plot2 <- df.ceco1 %>%
  ggplot(aes(x = dw_scaled, y = temp_max, color = model)) +
  labs(x = "Dry Weight (g)", y = "Maximum Temperature", color = "Model") +
  geom_point(size = 1, alpha = 0.6) +
  geom_abline(slope = -0.01672, intercept = 0.06771, color = "#F5A400", cex = 0.8, alpha = 0.8) +
  geom_abline(slope = -0.01672, intercept = -0.43875, color = "#7D0025", cex = 0.8, alpha = 0.8) +
  theme_bw() +
  scale_color_manual(values = c("#F5A400", "#7D0025")) +
  theme(axis.title = element_text(face = 'bold'),
        legend.title = element_text(face = 'bold'),
        #axis.title.x = element_blank(),
        legend.position = 'right')
temp_max.dw.plot2
```

### vs. LFM
Model:
```{r}
temp_max.lfm.noint <- lmer(temp_max ~ lfm + model + site + (1|individual), data = df.ceco1)
temp_max.lfm.int <- lmer(temp_max ~ lfm*model + site + (1|individual), data = df.ceco1)
performance(temp_max.lfm.noint)
# No interaction performs better
summary(temp_max.lfm.noint)
```

```{r}
temp_max.lfm.plot2 <- df.ceco1 %>%
  ggplot(aes(x = lfm, y = temp_max, color = model)) +
  labs(x = "Live Fuel Moisture", y = "Maximum Temperature", color = "Model") +
  geom_point(size = 1, alpha = 0.6) +
  geom_abline(slope = 0.006844, intercept = -0.450941, color = "#F5A400", cex = 0.8, alpha = 0.8) +
  geom_abline(slope = 0.006844, intercept = -0.950961, color = "#7D0025", cex = 0.8, alpha = 0.8) +
  theme_bw() +
  scale_color_manual(values = c("#F5A400", "#7D0025")) +
  theme(axis.title = element_text(face = 'bold'),
        legend.title = element_text(face = 'bold'),
        #axis.title.x = element_blank(),
        legend.position = 'right')
temp_max.lfm.plot2
```

### vs. MPa
Model:
```{r}
temp_max.mpa.noint <- lmer(temp_max ~ mpa + model + site + (1|individual), data = df.ceco1)
temp_max.mpa.int <- lmer(temp_max ~ mpa*model + site + (1|individual), data = df.ceco1)
performance(temp_max.mpa.noint)
# Interactions performs better
summary(temp_max.mpa.int)
```

```{r}
temp_max.mpa.plot2 <- df.ceco1 %>%
  ggplot(aes(x = mpa, y = temp_max, color = model)) +
  labs(x = "Water Potential (MPa)", y = "Maximum Temperature", color = "Model") +
  geom_point(size = 1, alpha = 0.6) +
  geom_abline(slope = -0.09389, intercept = -0.28836, color = "#F5A400", cex = 0.8, alpha = 0.8) +
  geom_abline(slope = 0.14742, intercept = 0.16285, color = "#7D0025", cex = 0.8, alpha = 0.8) +
  theme_bw() +
  scale_color_manual(values = c("#F5A400", "#7D0025")) +
  theme(axis.title = element_text(face = 'bold'),
        legend.title = element_text(face = 'bold'),
        #axis.title.x = element_blank(),
        legend.position = 'right')
temp_max.mpa.plot2
```

## FD
### vs. Dry Weight
Model:
```{r}
fd.dw.noint <- lmer(fd ~ dw_scaled + model + site + (1|individual), data = df.ceco1)
fd.dw.int <- lmer(fd ~ dw_scaled*model + site + (1|individual), data = df.ceco1)
performance(fd.dw.noint)
# No interaction performs better
summary(fd.dw.noint)
```

```{r}
fd.dw.plot2 <- df.ceco1 %>%
  ggplot(aes(x = dw_scaled, y = fd, color = model)) +
  labs(x = "Dry Weight (g)", y = "Flame Duration (s)", color = "Model") +
  geom_point(size = 1, alpha = 0.6) +
  geom_abline(slope = 0.2781, intercept = 0.1454, color = "#F5A400", cex = 0.8, alpha = 0.8) +
  geom_abline(slope = 0.2781, intercept = -0.639, color = "#7D0025", cex = 0.8, alpha = 0.8) +
  theme_bw() +
  scale_color_manual(values = c("#F5A400", "#7D0025")) +
  theme(axis.title = element_text(face = 'bold'),
        legend.title = element_text(face = 'bold'),
        #axis.title.x = element_blank(),
        legend.position = 'right')
fd.dw.plot2
```

### vs. LFM
Model:
```{r}
fd.lfm.noint <- lmer(fd ~ lfm + model + site + (1|individual), data = df.ceco1)
fd.lfm.int <- lmer(fd ~ lfm*model + site + (1|individual), data = df.ceco1)
performance(fd.lfm.int)
# No interaction performs better
summary(fd.lfm.noint)
```

```{r}
fd.lfm.plot2 <- df.ceco1 %>%
  ggplot(aes(x = lfm, y = fd, color = model)) +
  labs(x = "Live Fuel Moisture", y = "Flame Duration (s)", color = "Model") +
  geom_point(size = 1, alpha = 0.6) +
  geom_abline(slope = -0.004964, intercept = 0.594532, color = "#F5A400", cex = 0.8, alpha = 0.8) +
  geom_abline(slope = -0.004964, intercept = -0.297006, color = "#7D0025", cex = 0.8, alpha = 0.8) +
  theme_bw() +
  scale_color_manual(values = c("#F5A400", "#7D0025")) +
  theme(axis.title = element_text(face = 'bold'),
        legend.title = element_text(face = 'bold'),
        #axis.title.x = element_blank(),
        legend.position = 'right')
fd.lfm.plot2
```

### vs. MPa
Model:
```{r}
fd.mpa.noint <- lmer(fd ~ mpa + model + site + (1|individual), data = df.ceco1)
fd.mpa.int <- lmer(fd ~ mpa*model + site + (1|individual), data = df.ceco1)
performance(fd.mpa.int)
# At odds with each other (not sig. difference, lower AIC for interactions, lower BIC for no interactions), will lean towards including interaction term I suppose
summary(fd.mpa.int)
```

```{r}
fd.mpa.plot2 <- df.ceco1 %>%
  ggplot(aes(x = mpa, y = fd, color = model)) +
  labs(x = "Water Potential (MPa)", y = "Flame Duration (s)", color = "Model") +
  geom_point(size = 1, alpha = 0.6) +
  geom_abline(slope = -0.17857, intercept = -0.54351, color = "#F5A400", cex = 0.8, alpha = 0.8) +
  geom_abline(slope = -0.00656, intercept = -0.75701, color = "#7D0025", cex = 0.8, alpha = 0.8) +
  theme_bw() +
  scale_color_manual(values = c("#F5A400", "#7D0025")) +
  theme(axis.title = element_text(face = 'bold'),
        legend.title = element_text(face = 'bold'),
        #axis.title.x = element_blank(),
        legend.position = 'right')
fd.mpa.plot2
```
## Arranged
```{r}
ggarrange(tti.dw.plot2, tti.lfm.plot2, tti.mpa.plot2, ncol = 1, common.legend = T)

ggarrange(fh.dw.plot2, fh.lfm.plot2, fh.mpa.plot2, ncol = 1, common.legend = T)

ggarrange(temp_max.dw.plot2, temp_max.lfm.plot2, temp_max.mpa.plot2, ncol = 1, common.legend = T)

ggarrange(fd.dw.plot2, fd.lfm.plot2, fd.mpa.plot2, ncol = 1, common.legend = T)
```

# --------------------------------

# Species Differences: HP

## FH
### Dry Weight
```{r}
fhp1 <- ggplot(aes(x = dw_flam_sample, y = fh, color = spp), data = hp.df) +
  labs(x = "Dry Weight (g)", y = "Flame Height (cm)", color = "Species") +
  geom_point(size = 1, alpha = 0.7) +
  geom_smooth(method = "lm", se = FALSE) +
  theme_bw() +
  facet_wrap(~model) +
  scale_color_manual(values=c("#F5A400","#7D0025","#1165C1", "#EB5500")) +
  theme(axis.title = element_text(face = 'bold'),
        legend.title = element_text(face = 'bold'),
        #axis.title.x = element_blank(),
        legend.position = 'none')
fhp1
```

### LFM
```{r}
fhp2 <- ggplot(aes(x = lfm, y = fh, color = spp), data = hp.df) +
  labs(x = "Live Fuel Moisture (%)", y = "Flame Height (cm)", color = "Species") +
  geom_point(size = 1, alpha = 0.7) +
  geom_smooth(method = "lm", se = FALSE) +
  theme_bw() +
  facet_wrap(~model) +
  scale_color_manual(values=c("#F5A400","#7D0025","#1165C1", "#EB5500")) +
  theme(axis.title = element_text(face = 'bold'),
        legend.title = element_text(face = 'bold'),
        #axis.title.x = element_blank(),
        legend.position = 'none')
fhp2
```

### Water Potential
```{r}
fhp3 <- ggplot(aes(x = mpa, y = fh, color = spp), data = hp.df) +
  labs(x = "Water Potential (MPa)", y = "Flame Height (cm)", color = "Species") +
  geom_point(size = 1, alpha = 0.7) +
  geom_smooth(method = "lm", se = FALSE) +
  theme_bw() +
  facet_wrap(~model) +
  scale_color_manual(values=c("#F5A400","#7D0025","#1165C1", "#EB5500")) +
  theme(axis.title = element_text(face = 'bold'),
        legend.title = element_text(face = 'bold'),
        #axis.title.x = element_blank(),
        legend.position = 'none')
fhp3
```

## FD
### Dry Weight
```{r}
fdp1 <- ggplot(aes(x = dw_flam_sample, y = fd, color = spp), data = hp.df) +
  labs(x = "Dry Weight (g)", y = "Flame Duration (s)", color = "Species") +
  geom_point(size = 1, alpha = 0.7) +
  geom_smooth(method = "lm", se = FALSE) +
  theme_bw() +
  facet_wrap(~model) +
  scale_color_manual(values=c("#F5A400","#7D0025","#1165C1", "#EB5500")) +
  theme(axis.title = element_text(face = 'bold'),
        legend.title = element_text(face = 'bold'),
        #axis.title.x = element_blank(),
        legend.position = 'none')
fdp1
```

### LFM
```{r}
fdp2 <- ggplot(aes(x = lfm, y = fd, color = spp), data = hp.df) +
  labs(x = "Live Fuel Moisture (%)", y = "Flame Duration (s)", color = "Species") +
  geom_point(size = 1, alpha = 0.7) +
  geom_smooth(method = "lm", se = FALSE) +
  theme_bw() +
  facet_wrap(~model) +
  scale_color_manual(values=c("#F5A400","#7D0025","#1165C1", "#EB5500")) +
  theme(axis.title = element_text(face = 'bold'),
        legend.title = element_text(face = 'bold'),
        #axis.title.x = element_blank(),
        legend.position = 'none')
fdp2
```

### Water Potential
```{r}
fdp3 <- ggplot(aes(x = mpa, y = fd, color = spp), data = hp.df) +
  labs(x = "Water Potential (MPa)", y = "Flame Duration (s)", color = "Species") +
  geom_point(size = 1, alpha = 0.7) +
  geom_smooth(method = "lm", se = FALSE) +
  theme_bw() +
  facet_wrap(~model) +
  scale_color_manual(values=c("#F5A400","#7D0025","#1165C1", "#EB5500")) +
  theme(axis.title = element_text(face = 'bold'),
        legend.title = element_text(face = 'bold'),
        #axis.title.x = element_blank(),
        legend.position = 'none')
fdp3
```

## Max. Temp.
### Dry Weight
```{r}
mtp1 <- ggplot(aes(x = dw_flam_sample, y = temp_max, color = spp), data = hp.df) +
  labs(x = "Dry Weight (g)", y = "Maximum Temp.", color = "Species") +
  geom_point(size = 1, alpha = 0.7) +
  geom_smooth(method = "lm", se = FALSE) +
  theme_bw() +
  facet_wrap(~model) +
  scale_color_manual(values=c("#F5A400","#7D0025","#1165C1", "#EB5500")) +
  theme(axis.title = element_text(face = 'bold'),
        legend.title = element_text(face = 'bold'),
        #axis.title.x = element_blank(),
        legend.position = 'none')
mtp1
```

### LFM
```{r}
mtp2 <- ggplot(aes(x = lfm, y = temp_max, color = spp), data = hp.df) +
  labs(x = "Live Fuel Moisture (%)", y = "Maximum Temp.", color = "Species") +
  geom_point(size = 1, alpha = 0.7) +
  geom_smooth(method = "lm", se = FALSE) +
  theme_bw() +
  facet_wrap(~model) +
  scale_color_manual(values=c("#F5A400","#7D0025","#1165C1", "#EB5500")) +
  theme(axis.title = element_text(face = 'bold'),
        legend.title = element_text(face = 'bold'),
        #axis.title.x = element_blank(),
        legend.position = 'none')
mtp2
```

### Water Potential
```{r}
mtp3 <- ggplot(aes(x = mpa, y = temp_max, color = spp), data = hp.df) +
  labs(x = "Water Potential (MPa)", y = "Maximum Temp.", color = "Species") +
  geom_point(size = 1, alpha = 0.7) +
  geom_smooth(method = "lm", se = FALSE) +
  theme_bw() +
  facet_wrap(~model) +
  scale_color_manual(values=c("#F5A400","#7D0025","#1165C1", "#EB5500")) +
  theme(axis.title = element_text(face = 'bold'),
        legend.title = element_text(face = 'bold'),
        #axis.title.x = element_blank(),
        legend.position = 'none')
```

# Species Differences: EPI
## FH
### Dry Weight
```{r}
fhp4 <- ggplot(aes(x = dw_flam_sample, y = fh, color = spp), data = epi.df) +
  labs(x = "Dry Weight (g)", y = "Flame Height (cm)", color = "Species") +
  geom_point(size = 1, alpha = 0.7) +
  geom_smooth(method = "lm", se = FALSE) +
  theme_bw() +
  facet_wrap(~model) +
  scale_color_manual(values=c("#F5A400","#7D0025","#1165C1", "#EB5500")) +
  theme(axis.title = element_text(face = 'bold'),
        legend.title = element_text(face = 'bold'),
        #axis.title.x = element_blank(),
        legend.position = 'none')
fhp4
```

### LFM
```{r}
fhp5 <- ggplot(aes(x = lfm, y = fh, color = spp), data = epi.df) +
  labs(x = "Live Fuel Moisture (%)", y = "Flame Height (cm)", color = "Species") +
  geom_point(size = 1, alpha = 0.7) +
  geom_smooth(method = "lm", se = FALSE) +
  theme_bw() +
  facet_wrap(~model) +
  scale_color_manual(values=c("#F5A400","#7D0025","#1165C1", "#EB5500")) +
  theme(axis.title = element_text(face = 'bold'),
        legend.title = element_text(face = 'bold'),
        #axis.title.x = element_blank(),
        legend.position = 'none')
fhp5
```

### Water Potential
```{r}
fhp6 <- ggplot(aes(x = mpa, y = fh, color = spp), data = epi.df) +
  labs(x = "Water Potential (MPa)", y = "Flame Height (cm)", color = "Species") +
  geom_point(size = 1, alpha = 0.7) +
  geom_smooth(method = "lm", se = FALSE) +
  theme_bw() +
  facet_wrap(~model) +
  scale_color_manual(values=c("#F5A400","#7D0025","#1165C1", "#EB5500")) +
  theme(axis.title = element_text(face = 'bold'),
        legend.title = element_text(face = 'bold'),
        #axis.title.x = element_blank(),
        legend.position = 'none')
fhp6
```

## FD
### Dry Weight
```{r}
fdp4 <- ggplot(aes(x = dw_flam_sample, y = fd, color = spp), data = epi.df) +
  labs(x = "Dry Weight (g)", y = "Flame Duration (s)", color = "Species") +
  geom_point(size = 1, alpha = 0.7) +
  geom_smooth(method = "lm", se = FALSE) +
  theme_bw() +
  facet_wrap(~model) +
  scale_color_manual(values=c("#F5A400","#7D0025","#1165C1", "#EB5500")) +
  theme(axis.title = element_text(face = 'bold'),
        legend.title = element_text(face = 'bold'),
        #axis.title.x = element_blank(),
        legend.position = 'none')
fdp4
```

### LFM
```{r}
fdp5<-ggplot(aes(x = lfm, y = fd, color = spp), data = epi.df) +
  labs(x = "Live Fuel Moisture (%)", y = "Flame Duration (s)", color = "Species") +
  geom_point(size = 1, alpha = 0.7) +
  geom_smooth(method = "lm", se = FALSE) +
  theme_bw() +
  facet_wrap(~model) +
  scale_color_manual(values=c("#F5A400","#7D0025","#1165C1", "#EB5500")) +
  theme(axis.title = element_text(face = 'bold'),
        legend.title = element_text(face = 'bold'),
        #axis.title.x = element_blank(),
        legend.position = 'none')
fdp5
```

### Water Potential
```{r}
fdp6 <- ggplot(aes(x = mpa, y = fd, color = spp), data = epi.df) +
  labs(x = "Water Potential (MPa)", y = "Flame Duration (s)", color = "Species") +
  geom_point(size = 1, alpha = 0.7) +
  geom_smooth(method = "lm", se = FALSE) +
  theme_bw() +
  facet_wrap(~model) +
  scale_color_manual(values=c("#F5A400","#7D0025","#1165C1", "#EB5500")) +
  theme(axis.title = element_text(face = 'bold'),
        legend.title = element_text(face = 'bold'),
        #axis.title.x = element_blank(),
        legend.position = 'none')
fdp6
```

## Max. Temp.
### Dry Weight
```{r}
mtp4<-ggplot(aes(x = dw_flam_sample, y = temp_max, color = spp), data = epi.df) +
  labs(x = "Dry Weight (g)", y = "Maximum Temp.", color = "Species") +
  geom_point(size = 1, alpha = 0.7) +
  geom_smooth(method = "lm", se = FALSE) +
  theme_bw() +
  facet_wrap(~model) +
  scale_color_manual(values=c("#F5A400","#7D0025","#1165C1", "#EB5500")) +
  theme(axis.title = element_text(face = 'bold'),
        legend.title = element_text(face = 'bold'),
        #axis.title.x = element_blank(),
        legend.position = 'none')
mtp4
```

### LFM
```{r}
mtp5 <- ggplot(aes(x = lfm, y = temp_max, color = spp), data = epi.df) +
  labs(x = "Live Fuel Moisture (%)", y = "Maximum Temp.", color = "Species") +
  geom_point(size = 1, alpha = 0.7) +
  geom_smooth(method = "lm", se = FALSE) +
  theme_bw() +
  facet_wrap(~model) +
  scale_color_manual(values=c("#F5A400","#7D0025","#1165C1", "#EB5500")) +
  theme(axis.title = element_text(face = 'bold'),
        legend.title = element_text(face = 'bold'),
        #axis.title.x = element_blank(),
        legend.position = 'none')
mtp5
```

### Water Potential
```{r}
mtp6 <- ggplot(aes(x = mpa, y = temp_max, color = spp), data = epi.df) +
  labs(x = "Water Potential (MPa)", y = "Maximum Temp.", color = "Species") +
  geom_point(size = 1, alpha = 0.7) +
  geom_smooth(method = "lm", se = FALSE) +
  theme_bw() +
  facet_wrap(~model) +
  scale_color_manual(values=c("#F5A400","#7D0025","#1165C1", "#EB5500")) +
  theme(axis.title = element_text(face = 'bold'),
        legend.title = element_text(face = 'bold'),
        #axis.title.x = element_blank(),
        legend.position = 'none')
mtp6
```


# Arranging Plots
```{r}
ggarrange(fhp1, fhp4, fhp2, fhp5, fhp3, fhp6, common.legend = T, ncol =2, nrow = 3)

ggarrange(fdp1, fdp4, fdp2, fdp5, fdp3, fdp6, common.legend = T, ncol =2, nrow = 3)

ggarrange(mtp1, mtp4, mtp2, mtp5, mtp3, mtp6, common.legend = T, ncol =2, nrow = 3)
```